---
title: "ggfortify"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggfortify)
```

autoplot.stepfun

autoplot.varprd
Autoplot vars::varprd

#### Description 
 
Autoplot vars::varprd

#### Usage 
<pre><code>
## S3 method for class 'varprd'
autoplot(object, is.date = NULL, ts.connect = TRUE,
scales = "free_y", predict.geom = "line", predict.colour = "#0000FF",
predict.size = NULL, predict.linetype = NULL, predict.alpha = NULL,
predict.fill = NULL, predict.shape = NULL, conf.int = TRUE,
conf.int.colour = "#0000FF", conf.int.linetype = "none",
conf.int.fill = "#000000", conf.int.alpha = 0.3, ...)
</code></pre>

#### Arguments 
 
object vars::varpred instance
is.date Logical frag indicates whether the stats::ts is date or not. If not provided,
regard the input as date when the frequency is 4 or 12.
ts.connect Logical frag indicates whether connects original time-series and predicted val-
ues
scales Scale value passed to ggplot2cbind_wraps
predict.geom
35
geometric string for predicted time-series
* ``predict.colour``: line colour for predicted time-series
predict.size
point size for predicted time-series
predict.linetype
line type for predicted time-series
* ``predict.alpha``: alpha for predicted time-series
* ``predict.fill``: fill colour for predicted time-series
predict.shape point shape for predicted time-series
conf.int
Logical flag indicating whether to plot confidence intervals
conf.int.colour
line colour for confidence intervals
conf.int.linetype
line type for confidence intervals
conf.int.fill
fill colour for confidence intervals
* ``conf.int.alpha``: alpha for confidence intervals
...
* ``...``: other arguments passed to autoplot.ts
Value
ggplot

#### Examples 
```{r}
data(Canada, package = 'vars')
d.var <- vars::VAR(Canada, p = 3, type = 'const')
autoplot(stats::predict(d.var, n.ahead = 50), is.date = TRUE)
autoplot(stats::predict(d.var, n.ahead = 50), conf.int = FALSE)
```
cbind_wraps
Wrapper for cbind

#### Description 
 
Wrapper for cbind

#### Usage 
 <pre><code>
cbind_wraps(df1, df2)
</code></pre>
#### Arguments 
 
df1 1st data
df2 2nd data36
confint.acf
Value
list

#### Examples 
```{r}
ggfortify:::cbind_wraps(iris[1:2], iris[3:5])
```

check_names
Check data names are equal with expected

#### Description 
 
Check data names are equal with expected

#### Usage 
<pre><code>
check_names(data, expected)
</code></pre>

#### Arguments 
 
data list instance to be checked
expected expected character vector
Value
logical
confint.acf
Calcurate confidence interval for stats::acf

#### Description 
 
Calcurate confidence interval for stats::acf

#### Usage 
<pre><code>
## S3 method for class 'acf'
confint(x, ci = 0.95, ci.type = "white")
</code></pre>

#### Arguments 
 
* x stats::acf instance
* ci Float value for confidence interval
* ci.type "white" or "ma"

Value
vector

#### Examples 
```{r}
air.acf <- acf(AirPassengers, plot = FALSE)
ggfortify:::confint.acf(air.acf)
ggfortify:::confint.acf(air.acf, ci.type = 'ma')
```

deprecate.warning
Show deprecate warning

#### Description 
 
Show deprecate warning

#### Usage 
<pre><code>
deprecate.warning(old.kw, new.kw)
</code></pre>

#### Arguments 

* old.kw Keyword being deprecated
* ew.kw Keyword being replaced

#### Examples 
```{r}
ggfortify:::deprecate.warning('old', 'new')
```

fitted.ar
Calcurate fitted values for stats::ar

#### Description 
 
Calcurate fitted values for stats::ar

#### Usage 
<pre><code>
## S3 method for class 'ar'
fitted(object, ...)
</code></pre>

#### Arguments 
 
object stats::ar instance
... other keywords38
fortify.aareg
Value
ts An time series of the one-step forecasts

#### Examples 

fitted(ar(WWWUsage ))
flatten
Flatten dataframe contains matrix

#### Description 
 
tains list or matrix as column

#### Usage 
<pre><code>
flatten(df)
</code><pre>

#### Arguments 
 
df
