---
title: "``ggfortify::autoplot``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggfortify)
```

autoplot.aareg Autoplot survival::aareg

#### Description 
 
Autoplot survival::aareg

#### Usage 
<pre><code>
## S3 method for class 'aareg'
autoplot(object, maxtime = NULL, surv.connect = TRUE,
facets = TRUE, ncol = NULL, xlab = "", ylab = "", ...)
</code></pre>

#### Arguments 
 
* ``object``: survival::aareg instance
* ``maxtime``: truncate the input to the model at time "maxtime"
* ``surv.connect``: logical frag indicates whether connects survival curve to the origin
* ``facets``: Logical value to specify use facets
* ``ncol``: Number of facet/subplot columns
* ``xlab``: character vector or expression for x axis label
* ``ylab``: character vector or expression for y axis label
* ``...``: other arguments passed to autoplot.survfit

Value
ggplot

#### Examples 
```{r}
library(survival)
autoplot(aareg(Surv(time, status) ~ age + sex + ph.ecog, data = lung, nmin = 1))
```

