---
title: "``autoplot.density``Autoplot stats::density"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggfortify)
```
#### Description 
 
Autoplot stats::density

#### Usage 
<pre><code>
## S3 method for class 'density'
autoplot(object, p = NULL, colour = "#000000",
  linetype = NULL, fill = NULL, alpha = NULL, xlim = c(NA, NA),
  ylim = c(NA, NA), log = "", main = NULL, xlab = NULL, ylab = NULL,
  asp = NULL, ...)
</code></pre>
#### Arguments 
* ``object``: ***stats::density*** instance
* ``p``: ggplot2::ggplot instance to plot
* ``colour``: Line colour
* ``linetype``: Line type
* ``fill``: Fill colour
* ``alpha``: Alpha
* ``xlim``: limits for x axis
* ``ylim``: limits for y axis
* ``log``: which variables to log transform ("x", "y", or "xy")
* ``main``: character vector or expression for plot title
* ``xlab``: character vector or expression for x axis label
* ``ylab``: character vector or expression for y axis label
* ``asp``: the y/x aspect ratio
* ``...``: other arguments passed to PDC/CDF func

#### Value
ggplot

#### Examples 
```{r}
autoplot(stats::density(stats::rnorm(1:50)))
```
```{r}
autoplot(stats::density(stats::rnorm(1:50)), fill = 'blue')
```
