---
title: "``ggfortify::fortify.cpt``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggfortify)
```

#### Description 
 
Convert changepoint::cpt and strucchange::breakpoints to data.frame

#### Usage 
<pre><code>
## S3 method for class 'cpt'
fortify(model, data = NULL, is.date = NULL, ...)
</code></pre>


#### Arguments 
 
* ``	model	``: 	chantepoint::cpt or strucchange::breakpoints instance
* ``	data	``: 	original dataset, if needed
* ``	is.date	``: 	Logical frag indicates whether the stats::ts is date or not. If not provided, regard the input as date when the frequency is 4 or 12.
* ``	...	``: 	other arguments   passed to methods

Value
data.frame

#### Examples 
```{r}
library(changepoint)
fortify(cpt.mean(AirPassengers))
fortify(cpt.var(AirPassengers))
fortify(cpt.meanvar(AirPassengers))
library(strucchange)
bp.nile <- breakpoints(Nile ~ 1)
fortify(bp.nile)
fortify(breakpoints(bp.nile, breaks = 2))
fortify(breakpoints(bp.nile, breaks = 2), data = Nile)
```

