---
title: "autoplots"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggfortify)
```


autoplot.basis
Autoplot spline basis instances

#### Description 
 
Autoplot spline basis instances

#### Usage 
<pre><code>
## S3 method for class 'basis'
autoplot(object, data, n = 256, ...)
</code></pre>

#### Arguments 
 
* ``object``: spline basis object
* ``data``: x-values at which to evaluate the splines. Optional. By default, an evenly spaced sequence of 256 values covering the range of the splines will be used.
* ``n``: If data is not provided, instead use an evenly-spaced sequence of x-values of this length (plus one, since both endpoints are included). If data is provided, this argument is ignored.
* ``...``: Ignored.

Value
ggplot

#### Examples 
```{r}
library(splines)
x <- seq(0, 1, by=0.001)
spl <- bs(x, df=6)
autoplot(spl)
autoplot(spl, n=5)
```
autoplot.breakpoints
Autoplot strucchange::breakpoints

#### Description 
 
Autoplot strucchange::breakpoints

#### Usage 
<pre><code>
## S3 method for class 'breakpoints'
autoplot(object, data = NULL, cpt.colour = "#FF0000",
cpt.linetype = "dashed", ...)
</code></pre>


#### Arguments 
* ``object``: strucchange::breakpoints or strucchange::breakpointsfull instance.
* ``data``: Original time series. Mandatory for plotting strucchange::breakpoints instance.
* ``cpt.colour``: Line colour for changepoints
* ``cpt.linetype``: Line type for changepoints
* ``...``: other arguments passed to autoplot.ts

Value
ggplot

#### Examples 
```{r}
library(strucchange)
bp.nile <- breakpoints(Nile ~ 1)
autoplot(bp.nile)
autoplot(bp.nile, is.date = TRUE)
autoplot(breakpoints(bp.nile, breaks = 2), data = Nile)

```
autoplot.cpt
Autoplot changepoint::cpt

#### Description 
 
Autoplot changepoint::cpt

#### Usage 
<pre><code>
## S3 method for class 'cpt'
autoplot(object, is.date = NULL, cpt.colour = "#FF0000",
cpt.linetype = "dashed", ...)
</code></pre>

#### Arguments 
 
* ``	object 	``: 	changepoint::cpt instance
* ``	is.date 	``: 	Logical frag indicates whether the stats::ts is date or not. If not provided, regard the input as date when the frequency is 4 or 12.
* ``	cpt.colour 	``: 	Line colour for changepoints
* ``	cpt.linetype 	``: 	Line type for changepoints
* ``	... 	``: 	other arguments passed autoplot.ts

Value
ggplot

#### Examples 
```{r}
library(changepoint)
autoplot(cpt.mean(AirPassengers))
autoplot(cpt.meanvar(AirPassengers))

```
autoplot.cv.glmnet

Autoplot glmnet::cv.glmnet

#### Description 
 
Autoplot glmnet::cv.glmnet

#### Usage 
<pre><code>
## S3 method for class 'cv.glmnet'
autoplot(object, sign.lambda = 1, label.n = 12, label = TRUE, label.label = "nz", label.colour = NULL,
label.alpha = NULL, label.size = NULL, label.angle = NULL, label.family = NULL, label.fontface = NULL, label.lineheight = NULL, label.hjust = NULL, label.vjust = NULL, label.repel = FALSE,
xlim = c(NA, NA), ylim = c(NA, NA), log = "", main = NULL, xlab = NULL, ylab = NULL, asp = NULL, ...)
</code></pre>

#### Arguments 
 
* ``object 	``: 	glmnet::cv.glmnet instance
* ``sign.lambda ``: 	Either plot against log(lambda) (default) or its negative if sign.lambda=-1.
* ``label.n ``: 	Number of Df labels
* ``label ``: 	Logical value whether to display labels
* ``label.label 	``: 	Column name used for label text
* ``label.colour 	``: 	Colour for text labels
* ``label.alpha 	``: 	Alpha for text labels
* ``label.size ``: 	Size for text labels
* ``label.angle	``: 	Angle for text labels
* ``label.family 	``: 	Font family for text labels
* ``label.fontface	``: 	Fontface for text labels
* ``label.lineheight	``: 	Lineheight for text labels
* ``label.hjust	``: 	Horizontal adjustment for text labels
* ``label.vjust	``: 	Vertical adjustment for text labels
* ``label.repel	``: 	Logical flag indicating whether to use ggrepel, enabling this may take some time for plotting
* ``	xlim ``: 	limits for x axis
* ``	ylim	``: 	limits for y axis
* ``	log 	``: 	which variables to log transform ("x", "y", or "xy") main character vector or expression for plot title
* ``	xlab 	``: 	character vector or expression for x axis label
* ``	ylab 	``: 	character vector or expression for y axis label
* ``	asp 	``: 	the y/x aspect ratio
* ``	... 	``: 	other arguments passed to methods

Value
ggplot

#### Examples 
```{r}
autoplot(glmnet::cv.glmnet(data.matrix(Orange[-3]), data.matrix(Orange[3])))
```