---
title: "``autoplots"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggfortify)
```

Autoplot maps::map

#### Description 
 
Autoplot maps::map

#### Usage 
<pre><code>
## S3 method for class 'map'
autoplot(object, p = NULL, geom = "path", group = "group",
colour = "black", size = NULL, linetype = NULL, alpha = NULL,
fill = NULL, shape = NULL, xlim = c(NA, NA), ylim = c(NA, NA),
log = "", main = NULL, xlab = "", ylab = "", asp = NULL, ...)
</code><pre>

#### Arguments 
 
* ``	object 	``: 	maps::map instance
* ``	p 	``: 	ggplot2::ggplot instance
* ``	geom 	``: 	geometric string for map. ***path*** , ***point*** or ***polygon***
* ``	group 	``: 	key for grouping geoms
* ``	colour 	``: 	line colour
* ``	size 	``: 	point size
* ``	linetype 	``: 	line type
* ``	alpha	``: 	alpha
* ``	fill	``: 	fill colour
* ``	shape	``: 	point shape
* ``	xlim	``: 	limits for x axis
* ``	ylim	``: 	limits for y axis
* ``	log	``: 	which variables to log transform ("x", "y", or "xy") main character vector or expression for plot title
* ``	xlab 	``: 	character vector or expression for x axis label
* ``	ylab 	``: 	character vector or expression for y axis label
* ``	asp	``: 	the y/x aspect ratio
* ``	... 	``: 	other arguments passed to methods

Value
ggplotautoplot.matrix
21
autoplot.matrix
Plot base::matrix

#### Description 
 
Plot base::matrix

#### Usage 
<pre><code>
## S3 method for class 'matrix'
autoplot(object, original = NULL, geom = "tile",
colour = NULL, size = NULL, alpha = NULL, fill = "#0000FF",
shape = NULL, label = FALSE, label.label = "rownames",
label.colour = colour, label.alpha = NULL, label.size = NULL,
label.angle = NULL, label.family = NULL, label.fontface = NULL,
label.lineheight = NULL, label.hjust = NULL, label.vjust = NULL,
label.repel = FALSE, scale = NULL, xlim = c(NA, NA), ylim = c(NA, NA),
log = "", main = NULL, xlab = NULL, ylab = NULL, asp = NULL, ...)
</code></pre>

#### Arguments 
 
* ``	object 	``: 	base::matrix instance
* ``	original 	``: 	Combined to data by column if provided. Intended to be used for stat functions which returns not containing original data.
* ``	geom 	``: 	Geometric string for plotting. ***tile*** or ***point***.
* ``	colour 	``: 	colour for points (***point*** only)
* ``	size	``: 	point size
* ``	alpha 	``: 	alpha
* ``	fill 	``: 	fill colour. Ignored if scale keyword is passed. (***tile*** Only)
* ``	shape 	``: 	point shape
* ``	label 	``: 	Logical value whether to display labels
* ``	label.label 	``: 	Column name used for label text
* ``	label.colour	``: 	Colour for text labels
* ``	label.alpha	``: 	Alpha for text labels
* ``	label.size	``: 	Size for text labels
* ``	label.angle 	``: 	Angle for text labels
* ``	label.family 	``: 	Font family for text labels
* ``	label.fontface 	``: 	Fontface for text labels
* ``	label.lineheight	``: 	Lineheight for text labels
* ``	label.hjust 	``: 	Horizontal adjustment for text labels
* ``	label.vjust 	``: 	Vertical adjustment for text labels
* ``	label.repel 	``: 	Logical flag indicating whether to use ggrepel, enabling this may take some time for plotting
* ``	scale (Deprecated) 	``: 	ggplot2::scale instance to plot. (***tile*** Only)
* ``	xlim 	``: 	limits for x axis
* ``	ylim 	``: 	limits for y axis
* ``	log 	``: 	which variables to log transform ("x", "y", or "xy")
* ``	xlab 	``: 	character vector or expression for x axis label
* ``	ylab 	``: 	character vector or expression for y axis label
* ``	asp 	``: 	the y/x aspect ratio
* ``	... 	``: 	other arguments passed to methods

Value
ggplot

#### Examples 
```{r}
autoplot(matrix(rnorm(20), nc = 5))
autoplot(matrix(rnorm(20), nc = 5), fill = 'red')
autoplot(matrix(rnorm(20), nc = 2), geom = 'point')

```
autoplot.MSM.lm
Autoplot MSwM::MSM.lm

#### Description 
 
Autoplot MSwM::MSM.lm

#### Usage 
<pre><code>
## S3 method for class 'MSM.lm'
autoplot(object, prob.colour = "#FF0000",
prob.linetype = "dashed", ...)
</code></pre>

#### Arguments 
* ``object`` MSwM::MSM.lm instance
* ``prob.colour`` Line colour for probabilities
* ``prob.linetype`` Line type for probabilities
* ``...`` other arguments passed to autoplot.ts

Value
ggplot
#### Examples 
```{r}
## Not run:
library(MSwM)
d <- data.frame(Data = c(rnorm(50, mean = -10), rnorm(50, mean = 10)),
exog = cos(seq(-pi/2, pi/2, length.out = 100)))
d.mswm <- MSwM::msmFit(lm(Data ~.-1, data = d), k=2, sw=rep(TRUE, 2),
control = list(parallelization = FALSE))
autoplot(d.mswm)
## End(Not run)
```
