---
title: "``fortify.performance``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggfortify)
```

Convert ROCR::performance objects to data.frame

#### Description 
 
Convert ROCR::performance objects to data.frame

#### Usage 
<pre><code>
## S3 method for class 'performance'
fortify(model, data = NULL, ...)
</code></pre>

#### Arguments 
 
* ``model``: performance instances
* ``data``: original dataset, if needed
* ``... ``: other arguments passed to methods
Value
data.frame
fortify.prcomp
Convert stats::prcomp, stats::princomp to data.frame

#### Description 
 
Convert stats::prcomp, stats::princomp to data.frame

#### Usage 
<pre><code>
## S3 method for class 'prcomp'
fortify(model, data = NULL, ...)
</code></pre>

#### Arguments 
 
* ``model``: stats::prcomp or stats::princomp instance
* ``data``: original dataset, if needed
* ``... ``: other arguments passed to methods
Value
data.frame

#### Examples 
```{r}
fortify(stats::prcomp(iris[-5]))
fortify(stats::prcomp(iris[-5]), data = iris)
fortify(stats::princomp(iris[-5]))
fortify(stats::princomp(iris[-5]), data = iris)
```

fortify.RasterCommon
Convert raster to data.frame

#### Description 
 
Convert raster to data.frame

#### Usage 
<pre><code>
## S3 method for class 'RasterCommon'
fortify(model, data = NULL, maxpixels = 1e+05,
rename = TRUE, ...)
</code></pre>

#### Arguments 
 
* ``model``: raster instances
* ``data``: original dataset, if needed
* ``maxpixels``: number of pixels for resampling
* ``rename``: logical flag indicating whether to rename coordinates to long and lat
* ``... ``: other arguments passed to methods
Value
data.frame


fortify.SpatialCommon Convert sp instances to data.frame.

#### Description 
 
Convert sp instances to data.frame.

#### Usage 
<pre><code>
## S3 method for class 'SpatialCommon'
fortify(model, data = NULL, rename = TRUE, ...)
</code></pre>

#### Arguments 
 
* model sp instances
* data original dataset, if needed
* rename logical flag indicating whether to rename coordinates to long and lat
* ``... ``: other arguments passed to methods

#### Value
data.frame

## ``fortify.spec``
Convert stats::spec to data.frame

#### Description 
 
Convert stats::spec to data.frame

#### Usage 
 <pre><code>
## S3 method for class 'spec'
fortify(model, data = NULL, ...)
</code></pre>


#### Arguments 
 
model stats::spec instance
data original dataset, if needed
* ``... ``: other arguments passed to methods
Value
data.frame

#### Examples 
```{r}
fortify(spectrum(AirPassengers))
fortify(stats::spec.ar(AirPassengers))
fortify(stats::spec.pgram(AirPassengers))52
fortify.survfit
```


fortify.stepfun
Convert stats::stepfun to data.frame


#### Description 
 
Convert stats::stepfun to data.frame

#### Usage 
<pre><code>
## S3 method for class 'stepfun'
fortify(model, data, ...)
</code></pre>

#### Arguments 
 
* ``model``: stats::stepfun instance
* ``data``: original dataset, if needed
* ``... ``: other arguments passed to methods
Value
data.frame

#### Examples 
```{r}
fortify(stepfun(c(1, 2, 3), c(4, 5, 6, 7)))
fortify(stepfun(c(1), c(4, 5)))
fortify(stepfun(c(1, 3, 4, 8), c(4, 5, 2, 3, 5)))
fortify(stepfun(c(1, 2, 3, 4, 5, 6, 7, 8, 10), c(4, 5, 6, 7, 8, 9, 10, 11, 12, 9)))
```

## ``fortify.survfit``
Convert survival::survfit to data.frame

#### Description 
 
Convert ``survival::survfit`` to data.frame

#### Usage 
<pre><code>
## S3 method for class 'survfit'
fortify(model, data = NULL, surv.connect = FALSE,
fun = NULL, ...)
</code><pre>


#### Arguments 
 
* ``model``: survival::survfit instance
* ``data``: original dataset, if needed
* ``surv.connect`` logical frag indicates whether connects survival curve to the origin
* ``fun``: an arbitrary function defining a transformation of the survival curve
* ``...``: other arguments passed to methods

#### Value
data.frame

#### Examples 
```{r}
library(survival)
fortify(survfit(Surv(time, status) ~ sex, data = lung))
fortify(survfit(Surv(time, status) ~ 1, data = lung))
fortify(survfit(coxph(Surv(time, status) ~ sex, data = lung)))
fortify(survfit(coxph(Surv(time, status) ~ 1, data = lung)))
```

## ``fortify.table``
Convert base::table to data.frame

#### Description 
 
Convert base::table to data.frame

#### Usage 
<pre><code>
## S3 method for class 'table'
fortify(model, data, ...)
</code></pre>

#### Arguments 
 
* model base::table instance
* data original dataset, if needed
* ``... ``: other arguments passed to methods

#### Value
data.frame

#### Examples 
```{r}
fortify(Titanic)
```
