Post process for fortify. Based on ggplot2::qplot

#### Description 
 
Post process for fortify. Based on ggplot2::qplot

#### Usage 
<pre><code>
post_autoplot(p, xlim = c(NA, NA), ylim = c(NA, NA), log = "",
main = NULL, xlab = NULL, ylab = NULL, asp = NULL)
</code></pre>

#### Arguments 
 
* ``	p 	``: 	ggplot2::ggplot instances
* ``	xlim 	``: 	limits for x axis
* ``	ylim	``: 	limits for y axis
* ``	log 	``: 	which variables to log transform ("x", "y", or "xy") main character vector or expression for plot title
* ``	xlab 	``: 	character vector or expression for x axis label
* ``	ylab 	``: 	character vector or expression for y axis label
* ``	asp 	``: 	the y/x aspect ratio


Value
data.frame

#### Examples 
```{r}
p <- qplot(Petal.Length, Petal.Width, data = iris)
ggfortify:::post_autoplot(p, xlim = c(1, 5), ylim = c(1, 5), log = 'xy', main = 'title',
xlab = 'x', ylab = 'y', asp = 1.5)
```

post_fortify
Post process for fortify.

#### Description 
 
Post process for fortify.

#### Usage 
 <pre><code>
post_fortify(data, klass = NULL)
</code></pre>


#### Arguments 
 
data
klass
data.frame
instance to be added as base_class attr, should be original model before fortified
Value
data.frame


## print,ggmultiplot-method
Generic print function for ggmultiplot

#### Description 
 
Generic print function for ggmultiplot

#### Usage 
<pre><code>
## S4 method for signature 'ggmultiplot'
print(x)
</code></pre>

#### Arguments 
 
x
rbind_ts
ggmultiplot
Rbind original and predicted time-series-like instances as fortified
data.frame

#### Description 
 
Rbind original and predicted time-series-like instances as fortified data.frame

#### Usage 
 <pre><code>
rbind_ts(data, original, ts.connect = TRUE, index.name = "Index",
data.name = "Data")

#### Arguments 
 
* ``	data	``: 	Original ts instance
* ``	original	``: 	Logical frag indicates whether connects original time-series and predicted vaues-
* ``	ts.connect	``: 	Specify column name for time series index
* ``	index.name	``: 	Specify column name for univariate time series data. Ignored in multivariate
* ``	data.name	``: 	Predicted/forecasted ts instance time series.
Value
data.frame

#### Examples 
```{r}
predicted <- predict(stats::HoltWinters(UKgas), n.ahead = 5, prediction.interval = TRUE)
rbind_ts(predicted, UKgas, ts.connect = TRUE)
```

residuals.ar
Calcurate residuals for stats::ar

#### Description 
 
Calcurate residuals for stats::ar

#### Usage 
<pre><code>
## S3 method for class 'ar'
residuals(object, ...)
</code></pre>

#### Arguments 
 
object stats::ar instance
... other keywords
Value
ts Residuals extracted from the object object.

#### Examples 
```{r}
residuals(ar(WWWUsage ))
```
show,ggmultiplot-method
Generic show function for ggmultiplot

#### Description 
 
Generic show function for ggmultiplot

#### Usage 
 <pre><code>
## S4 method for signature 'ggmultiplot'
show(object)
</code></pre>

#### Arguments 
 
object: ggmultiplot
support_autoplot: Check if passed object is supported by ggplot2::autoplot

#### Description 
 
Check if passed object is supported by ggplot2::autoplot

#### Usage 
<pre><code>
support_autoplot(obj)
</code></pre>


#### Arguments 
 
obj
object

Value
logical

unscale

Backtransform scale-ed object

#### Description 
 
Backtransform scale-ed object

#### Usage 
<pre><code>
unscale(data, center = NULL, scale = NULL)
</code></pre>

#### Arguments 
 

Value
data.frame

#### Examples 
```{r}
df <- iris[-5]
ggfortify::unscale(base::scale(df))
```