---
title: "ggfortify"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggfortify)
```

ggdistribution
Plot distribution

#### Description 
 
Plot distribution

#### Usage 
<pre><code>
ggdistribution(func, x, p = NULL, colour = "#000000", linetype = NULL,
fill = NULL, alpha = NULL, ...)
</code</pre>

#### Arguments 
 
* func PDF or CDF function
* x Numeric vector to be passed to func
* p ggplot2::ggplot instance to plot
* colour Line colour
* linetype Line type
* fill Fill colour
* alpha Alpha
* ... Keywords passed to PDC/CDF func

#### Value
ggplot

#### Examples 
```{r}
ggdistribution(dnorm, seq(-3, 3, 0.1), mean = 0, sd = 1)
ggdistribution(ppois, seq(0, 30), lambda = 20)
p <- ggdistribution(pchisq, 0:20, df = 7, fill = 'blue')
ggdistribution(pchisq, 0:20, p = p, df = 9, fill = 'red')
```

ggfortify
ggfortify
ggfortify

#### Description 
 
Define Fortify and Autoplot to Allow ’ggplot2’ to Draw Some Popular Packages
ggfreqplot
Plot seasonal subseries
stats::monthplot
of time series,
generalization

#### Description 
 
Plot seasonal subseries of time series, generalization of stats::monthplot

#### Usage 
<pre><code>
ggfreqplot(data, freq = NULL, nrow = NULL, ncol = NULL,
conf.int = FALSE, conf.int.colour = "#0000FF",
conf.int.linetype = "dashed", conf.int.fill = NULL,
conf.int.alpha = 0.3, conf.int.value = 0.95, facet.labeller = NULL, ...)
</code></pre>

#### Arguments 
 
* ``data ``: stats::ts instance
* ``freq ``: Length of frequency. If not provided, use time-series frequency
* ``nrow ``: Number of plot rows
* ``ncol ``: Number of plot columns
* ``conf.int ``: Logical flag indicating whether to plot confidence intervals
* ``conf.int.colour``: line colour for confidence intervals
* ``conf.int.linetype``: line type for confidence intervals
* ``conf.int.fill``: fill colour for confidence intervals
* ``conf.int.alpha``: alpha for confidence intervals
* ``conf.int.value``: Coverage probability for confidence interval
* ``facet.labeller``: A vector used as facet labels
...
Value
ggplot
Keywords passed to autoplot.ts

ggmultiplot-class

#### Examples 
```{r}
ggfreqplot(AirPassengers)
ggfreqplot(AirPassengers, freq = 4)
ggfreqplot(AirPassengers, conf.int = TRUE)
```

ggmultiplot-class
An S4 class to hold multiple ggplot2::ggplot instances

#### Description 
 
An S4 class to hold multiple ggplot2::ggplot instances

#### Usage 
<pre><code>
## S4 method for signature 'ggmultiplot'
length(x)
## S4 method for signature 'ggmultiplot,ANY,ANY,ANY'
x[i, j, ..., drop = TRUE]
## S4 method for signature 'ggmultiplot'
x[[i, j, ..., drop]]
## S4 replacement method for signature 'ggmultiplot'
x[i, j, ...] <- value
## S4 replacement method for signature 'ggmultiplot'
x[[i, j, ...]] <- value
</code></pre>

#### Arguments 
 
* x ggmultiplot
* i elements to extract or replace
* j not used
* ... not used
* drop not used
* value value to be set
* Slots: plots List of ggplot2::ggplot instances
* ncol Number of grid columns
* nrow Number of grid rowsggtsdiag

## ggtsdiag
67
Plots time-series diagnostics

#### Description 
 
Plots time-series diagnostics

#### Usage 
<pre><code>
ggtsdiag(object, gof.lag = 10, conf.int = TRUE,
conf.int.colour = "#0000FF", conf.int.linetype = "dashed",
conf.int.fill = NULL, conf.int.alpha = 0.3, ad.colour = "#888888",
ad.linetype = "dashed", ad.size = 0.2, nrow = NULL, ncol = 1, ...)
</code></pre>

#### Arguments 
 
* ``object``: A fitted time-series model
* ``gof.lag``: The maximum number of lags for a Portmanteau goodness-of-fit test
* ``conf.int``: Logical flag indicating whether to plot confidence intervals
* ``conf.int.colour``: line colour for confidence intervals
* ``conf.int.linetype``: line type for confidence intervals
* ``conf.int.fill``: fill colour for confidence intervals
* ``conf.int.alpha``: alpha for confidence intervals
* ``ad.colour``: Line colour for additional lines
* ``ad.linetype``: Line type for additional lines
* ``ad.size``: Fill colour for additional lines
* ``nrow``: Number of facet/subplot rows
* ``ncol``: Number of facet/subplot columns
* ``...``: other keywords


Value
ggplot

#### Examples 

ggtsdiag(arima(AirPassengers))68
infer
grid.draw.ggmultiplot The implemented grid.draw method for ggmultiplot, in order to work
with ggsave() properly

#### Description 
 
The implemented grid.draw method for ggmultiplot, in order to work with ggsave() properly

#### Usage 
<pre><code>
## S3 method for class 'ggmultiplot'
grid.draw(plot)
</code></pre>

#### Arguments 
 
plot
infer
ggmultiplot
Infer class name

#### Description 
 
Infer class name

#### Usage 
<pre><code>
infer(data)
</code></pre>

#### Arguments 
 
data
Value
character
list instanceis.univariate
is.univariate
69
Check if Validates number of ts variates

#### Description 
 
Check if Validates number of ts variates

#### Usage 
<pre><code>
is.univariate(data, raise = TRUE)
</code></pre>

#### Arguments 
 
data ts instance
raise Logical flag whether raise an error
Value
logical

#### Examples 
```{r}
ggfortify:::is.univariate(AirPassengers)
```


is_derived_from
Check object is target class, or object is data.frame fortified from
target.

#### Description 
 
Check object is target class, or object is data.frame fortified from target.

#### Usage 
<pre><code>
is_derived_from(object, target)
</code></pre>

#### Arguments 
 
object instance to be checked. For data.frame, check whether it is fortified from target
class
target class name
Value
logical70
plot_confint

#### Examples 
```{r}
ggfortify:::is_derived_from(prcomp(iris[-5]), 'prcomp')
```

plot_confint
Attach confidence interval to ggplot2::ggplot

#### Description 
 
Attach confidence interval to ggplot2::ggplot

#### Usage 
<pre><code>
plot_confint(p, data = NULL, lower = "lower", upper = "upper",
conf.int = TRUE, conf.int.geom = "line", conf.int.group = NULL,
conf.int.colour = "#0000FF", conf.int.linetype = "none",
conf.int.fill = "#000000", conf.int.alpha = 0.3)
</code></pre>

#### Arguments 
 
* ``p:`` ggplot2::ggplot instance
* ``data:`` data contains lower and upper confidence intervals
* ``lower:`` column name for lower confidence interval
* ``upper:`` column name for upper confidence interval
* ``conf.int:`` Logical flag indicating whether to plot confidence intervals
* ``conf.int.geom:``  geometric string for confidence interval. ’line’ or ’step’
* ``conf.int.group:``  name of grouping variable for confidence intervals
* ``conf.int.colour:``  line colour for confidence intervals
* ``conf.int.linetype::``  line type for confidence intervals
* ``conf.int.fill:``  fill colour for confidence intervals
* ``conf.int.alpha``: alpha for confidence intervals
Value
ggplot

#### Examples 
```{r}
d <- fortify(stats::acf(AirPassengers, plot = FALSE))
p <- ggplot(data = d, mapping = aes(x = Lag))
ggfortify:::plot_confint(p, data = d)
```


plot_label
plot_label
71
Attach label to ggplot2::ggplot

#### Description 
 
Attach label to ggplot2::ggplot

#### Usage 
<pre><code>
plot_label(p, data, x = NULL, y = NULL, label = TRUE, label.label = "rownames", label.colour = NULL, 
  label.alpha = NULL, label.size = NULL, label.angle = NULL, label.family = NULL,
  label.fontface = NULL, label.lineheight = NULL, label.hjust = NULL,
  label.vjust = NULL, label.repel = FALSE, label.show.legend = NA)
</code></pre>

#### Arguments 
* ``	P	``: 	ggplot2::ggplot instance
* ``	data 	``: 	Data contains text label
* ``	x 	``: 	x coordinates for label
* ``	y 	``: 	y coordinates for label
* ``	label 	``: 	Logical value whether to display labels
* ``	label.label 	``: 	Column name used for label text
* ``	label.colour 	``: 	Colour for text labels
* ``	label.alpha	``: 	Alpha for text labels
* ``	label.size 	``: 	Size for text labels
* ``	label.angle 	``: 	Angle for text labels
* ``	label.family 	``: 	Font family for text labels
* ``	label.fontface 	``: 	Fontface for text labels
* ``	label.lineheight	``: 	Lineheight for text labels
* ``	label.hjust 	``: 	Horizontal adjustment for text labels
* ``	label.vjust 	``: 	Vertical adjustment for text labels
* ``	label.repel	``: 	Logical flag indicating whether to use ggrepel, enabling this may take some time for plotting
* ``	label.show.legend	``: 	Logical value indicating whether to show the legend of the text labels

Value
ggplot72
post_fortify
post_autoplot
