---
title: "ggfortify"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggfortify)
```
fortify.glmnet
Convert glmnet::glmnet to data.frame

#### Description 
 
Convert glmnet::glmnet to data.frame

#### Usage 
<pre><code>
## S3 method for class 'glmnet'
fortify(model, data = NULL, ...)
</code></pre>

#### Arguments 
 
model glmnet::glmnet instance
data original dataset, if needed
* ``... ``: other arguments passed to methods
Value
data.frame

#### Examples 
```{r}
fortify(glmnet::glmnet(data.matrix(Orange[-3]), data.matrix(Orange[3])))
```

fortify.kmeans
Convert cluster instances to data.frame

#### Description 
 
Convert cluster instances to data.frame

#### Usage 
<pre><code>
## S3 method for class 'kmeans'
fortify(model, data = NULL, ...)
</code></pre>

#### Arguments 
 
model
data
...
Clustered instance
original dataset, if needed
other arguments passed to methods
Value
data.frame

#### Examples 
```{r}
fortify(stats::kmeans(iris[-5], 3))
fortify(stats::kmeans(iris[-5], 3), data = iris)
fortify(cluster::clara(iris[-5], 3))
fortify(cluster::fanny(iris[-5], 3))
fortify(cluster::pam(iris[-5], 3), data = iris)
```


fortify.lfda
Convert lfda::lfda or lfda::klfda or lfda::self to data.frame

#### Description 
 
Convert lfda::lfda or lfda::klfda or lfda::self to data.frame

#### Usage 
 <pre><code>
## S3 method for class 'lfda'
fortify(model, data = NULL, ...)
</code></pre>

#### Arguments 
 
model
data
...
lfda::lfda or lfda::klfda or lfda::self instance
original dataset, if needed
other arguments 
  passed to methods
  
Value
data.frame

#### Examples 
```{r}
## Not run:
model <- lfda::lfda(iris[, -5], iris[, 5], 3, metric = "plain")
fortify(model)
## End(Not run)
```
fortify.list
Convert list to data.frame

#### Description 
 
Convert list to data.frame

#### Usage 
 <pre><code>
## S3 method for class 'list'
fortify(model, data = NULL, ...)
</code></pre>

#### Arguments 
 
* model list instance
* data original dataset, if needed
* ``... ``: other arguments passed to methods
Value
data.frame
fortify.matrix
Convert base::matrix to data.frame

#### Description 
 
Different from as.data.frame

#### Usage 
 <pre><code>
## S3 method for class 'matrix'
fortify(model, data = NULL, compat = FALSE, ...)
</code></pre>


#### Arguments 
 
model
data
compat
...
base::matrix instance
original dataset, if needed
Logical frag to specify the behaviour when converting matrix which has no col-
umn name. If FALSE, result has character columns like c("1", "2", ...). If TRUE,
result has character columns like c("V1", "V2", ...).
other 
#### Arguments 
  passed to methods
Value
data.frame

#### Examples 
```{r}
fortify(matrix(1:6, nrow=2, ncol=3))
```

fortify.MSM.lm
Convert MSwM::MSM.lm to data.frame

#### Description 
 
Convert MSwM::MSM.lm to data.frame

#### Usage 
<pre><code>
## S3 method for class 'MSM.lm'
fortify(model, data = NULL, melt = FALSE, ...)
</code></pre>

#### Arguments 
 
model
data
melt
...
MSwM::MSM.lm instance
original dataset, if needed
Logical flag indicating whether to melt each models
other arguments passed to methods
Value
data.frame

#### Examples 
```{r}
library(MSwM)
d <- data.frame(Data = c(rnorm(50, mean = -10), rnorm(50, mean = 10)),
exog = cos(seq(-pi/2, pi/2, length.out = 100)))
d.mswm <- MSwM::msmFit(lm(Data ~.-1, data = d), k=2, sw=rep(TRUE, 2),
control = list(parallelization = FALSE))
fortify(d.mswm)
```