---
title: "``create_yaxis``:  Creating multiples yAxis for add a highcharts"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(highcharter)
library(dplyr)
library(magrittr)
```

#### Description 

Creating multiples yAxis for add a highcharts

#### Usage
<pre><code>
create_yaxis(naxis = 2, heights = 1, sep = 0.01, offset = 0, turnopposite = TRUE, ...)
</code></pre>

#### Arguments 

* ``naxis``: Number of axis an integer.
* ``heights``: A numeric vector. This values will be normalized.
* ``sep``: A numeric value for the separation (in percentage) for the panes.
* ``offset``: A numeric value (in percentage).
* ``turnopposite``: A logical value to turn the side of each axis or not.
* ``...``: Arguments defined in http://api.highcharts.com/highcharts#yAxis.

#### Examples
```{r}
highchart() %>%
  hc_yAxis_multiples(create_yaxis(naxis = 2, heights = c(2, 1))) %>%
  hc_add_series(data = c(1,3,2), yAxis = 0) %>%
  hc_add_series(data = c(20, 40, 10), yAxis = 1)
```
```{r}
highchart() %>%
  hc_yAxis_multiples(create_yaxis(naxis = 3, lineWidth = 2, title = list(text = NULL))) %>%
  hc_add_series(data = c(1,3,2)) %>%
  hc_add_series(data = c(20, 40, 10), yAxis = 1) %>%
  hc_add_series(data = c(200, 400, 500), type = "column", yAxis = 2) %>%
  hc_add_series(data = c(500, 300, 400), type = "column", yAxis = 2)
```