---
title: "``hc_plotOptions``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(highcharter)
library(dplyr)
library(magrittr)
```

### Adding plot options to highchart objects

#### Description 

The plotOptions is a wrapper object for config objects for each series type. The config objects for
each series can also be overridden for each series item as given in the series array.

#### Usage
<pre><code>
hc_plotOptions(hc, ...)
</code></pre>

#### Arguments 

* ``hc ``: A highchart htmlwidget object.
... Arguments are defined in http://api.highcharts.com/highcharts#plotOptions.


#### Examples
```{r}
data(citytemp)
hc <- highchart() %>%
hc_plotOptions(line = list(color = "blue",
  marker = list(
    fillColor = "white",
    lineWidth = 2,
    lineColor = NULL
   )
  )) %>%
hc_add_series(name = "Tokyo", data = citytemp$tokyo) %>%
hc_add_series(name = "London", data = citytemp$london, marker = list(fillColor = "black"))
hc
```
```{r}
# override the `blue` option with the explicit parameter
hc %>%
hc_add_series(name = "London",
data = citytemp$new_york,
color = "red")
```

####  Details

Configuration options for the series are given in three levels. Options for all series in a chart are
given with the hc_plotOptions function. Then options for all series of a specific type are given
in the plotOptions of that type, for example ``hc_plotOptions(line = list(...))``. Next, options
for one single series are given in the series array.
