---
title: "``hchart.survfit``: Plot survival curves using Highcharts"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(highcharter)
library(dplyr)
library(magrittr)
```



#### Description 

Plot survival curves using Highcharts

####  Usage 

<pre><code>
## S3 method for class 'survfit'
hchart(object, ..., fun = NULL, markTimes = TRUE,
symbol = "plus", markerColor = "black", ranges = FALSE,
rangesOpacity = 0.3)
</code></pre>

#### Arguments 

* ``object``: A survfit object as returned from the survfit function
* ``...``: Extra parameters to pass to hc_add_series function
* ``fun``: Name of function or function used to transform the survival curve: log will
put y axis on log scale, event plots cumulative events (f(y) = 1-y), cumhaz plots the cumulative hazard function (f(y) = -log(y)), and cloglog creates a complimentary log-log survival plot (f(y) = log(-log(y)) along with log scale for the x-axis.
* ``markTimes``: markTimes Label curves marked at each censoring time? TRUE by default
* ``symbol``: Symbol to use as marker (plus sign by default)
* ``markerColor``: Color of the marker ("black" by default); use NULL to use the respective color
of each series
* ``ranges``: Plot interval ranges? FALSE by default
* ``rangesOpacity``: Opacity of the interval ranges (0.3 by default)


#### Value
Highcharts object to plot survival curves

#### Examples 
 ```{r}
# Plot Kaplan-Meier curves
require("survival")
leukemia.surv <- survfit(Surv(time, status) ~ x, data = aml)
hchart(leukemia.surv)
```
```{r}
# Plot the cumulative hazard function
lsurv2 <- survfit(Surv(time, status) ~ x, aml, type='fleming')
hchart(lsurv2, fun="cumhaz")
```
```{r}
# Plot the fit of a Cox proportional hazards regression model
fit <- coxph(Surv(futime, fustat) ~ age, data = ovarian)
ovarian.surv <- survfit(fit, newdata=data.frame(age=60))
hchart(ovarian.surv, ranges = TRUE)
```
