
Add concentration ellipse around groups. R function stat_ellipse(). Key arguments: ?type: The type of ellipse. The default “t” assumes a multivariate t-distribution, and “norm” assumes a multivariate normal distribution. “euclid” draws a circle with the radius equal to level, representing the euclidean distance from the center.
?level: The confidence level at which to draw an ellipse (default is 0.95), or, if type=“euclid”, the radius of the circle to be drawn.
```{r}
b + geom_point(aes(color = cyl, shape = cyl))+
  stat_ellipse(aes(color = cyl), type = "t")+
  scale_color_manual(values = c("#00AFBB", "#E7B800", "#FC4E07"))
```

Instead of drawing the concentration ellipse, you can: i) plot a convex hull of a set of points; ii) add the mean points and the confidence ellipse of each group. Key R functions: stat_chull(), stat_conf_ellipse() and stat_mean() [in ggpubr]:
```{r}
# Convex hull of groups
b + geom_point(aes(color = cyl, shape = cyl)) +
  stat_chull(aes(color = cyl, fill = cyl), 
             alpha = 0.1, geom = "polygon") +
  scale_color_manual(values = c("#00AFBB", "#E7B800", "#FC4E07")) +
  scale_fill_manual(values = c("#00AFBB", "#E7B800", "#FC4E07")) 
  
```

```{r}
# Add mean points and confidence ellipses
b + geom_point(aes(color = cyl, shape = cyl)) +
  stat_conf_ellipse(aes(color = cyl, fill = cyl), 
                    alpha = 0.1, geom = "polygon") +
  stat_mean(aes(color = cyl, shape = cyl), size = 2) + 
  scale_color_manual(values = c("#00AFBB", "#E7B800", "#FC4E07")) +
  scale_fill_manual(values = c("#00AFBB", "#E7B800", "#FC4E07")) 
```
•Easy alternative using ggpubr. See this article: Perfect Scatter Plots with Correlation and Marginal Histograms
```{r}
# Add group mean points and stars
ggscatter(df, x = "wt", y = "mpg",
          color = "cyl", palette = "npg",
          shape = "cyl", ellipse = TRUE, 
          mean.point = TRUE, star.plot = TRUE,
          ggtheme = theme_minimal())
# Change the ellipse type to 'convex'
ggscatter(df, x = "wt", y = "mpg",
          color = "cyl", palette = "npg",
          shape = "cyl",
          ellipse = TRUE, ellipse.type = "convex",
          ggtheme = theme_minimal())
```
