 plotly Sign In SIGN UP  + NEW PROJECT  UPGRADE  REQUEST DEMO Feed Pricing Dashboards API
Plotly for R is now entirely open source, free, and self-hosted
Learn more about why we've open sourced

 HELP/API LIBRARIES/R/GETTING STARTED WITH PLOTLY FOR R FORK ON GITHUB
Getting Started with Plotly for R
Plotly is an R package for creating interactive web-based graphs via the open source JavaScript graphing library plotly.js. As of version 2.0 (November 17, 2015), Plotly graphs are rendered locally through the htmlwidgets framework.

 Build Status

INSTALLATION

Plotly is now on CRAN!

install.packages("plotly")

Or install the latest development version (on GitHub) via devtools:

# install.packages("devtools")
devtools::install_github("ropensci/plotly")

RStudio users should download the latest RStudio release for compatibility with htmlwidgets.

SIMPLE EXAMPLE

library(plotly)
p <- plot_ly(midwest, x = percollege, color = state, type = "box")
p
Simply printing the plotly object will render the chart locally in your web browser or in the R Studio viewer.


Plotly graphs are interactive. Click on legend entries to toggle traces, click-and-drag on the chart to zoom, double-click to autoscale, shift-and-drag to pan.

HOSTING GRAPHS IN YOUR ONLINE PLOTLY ACCOUNT

By default, plotly for R runs locally in your web browser or in the R Studio viewer. You can publish your charts to the web with plotly's web service.

1 - Create a free plotly account

A plotly account is required to publish charts online. It's free to get started, and you control the privacy of your charts.

2 - Save your authentication credentials

Find your authentication API keys in your online settings. Set them in your R session with:

Sys.setenv("plotly_username"="your_plotly_username")
Sys.setenv("plotly_api_key"="your_api_key")
Save these commands in your .Rprofile file to be run everytime you start R.

3 - Publish your graphs to plotly with plotly_POST

library(plotly)
p <- plot_ly(midwest, x = percollege, color = state, type = "box")
plotly_POST(p, filename = "r-docs/midwest-boxplots", world_readable=TRUE)
filename sets the name of the file inside your online plotly account.

world_readable sets the privacy of your chart. If TRUE, the graph is publically viewable, if FALSE, only you can view it.

SPECIAL INSTRUCTIONS FOR PLOTLY ON-PREMISE USERS

Your API key for account on the public cloud will be different than the API key in Plotly On-Premise. Visit https://plotly.your-company.com/settings/api/ to find your Plotly On-Premise API key. Remember to replace "your-company.com" with the URL of your Plotly On-Premise server.

If your company has a Plotly On-Premise server, change the R API endpoint so that it points to your company's Plotly server instead of Plotly's cloud.

In your .RProfile write:

Sys.setenv("plotly_domain"="https://plotly.your-company.com")  
Sys.setenv("plotly_api_domain" = "https://api-plotly.your-company.com")
Remember to replace "your-company" with the URL of your Plotly On-Premise server.

MAKE YOUR FIRST GRAPH
upgrade to pro
unlimited private files & email support
$20 PER MONTH
API

Documentation
API Libraries
REST APIs
Plotly.js
Hardware
ABOUT US

Team
Careers
Plotly Blog
Modern Data
HELP

Knowledge Base
Benchmarks
Workshop
SOLUTIONS

Plans & Pricing
Enterprise
Education
Plotly.js
CONNECT

    
Copyright © 2015 Plotly. All rights reserved.

Terms of Service

Privacy Policy

