```{r}
library(gapminder)
library(ggplot2)
```


1. Box Plots and Relations
2. Boxplots
3. Violin Plots
4. Beeswarm Plots
5. Effectiveness and Scalability
6. Ridge Plots

## Boxplots
Boxplots, or box-and-whisker plots, provide a skeletal representation of a distribution.

They are very well suited for showing distributions for multiple groups.

There are many variations of boxplots:

Most start with a box from the first to the third quartiles and divided by the median.

The simplest form then adds a whisker from the lower quartile to the minimum and from the upper quartile to the maximum.

More common is to draw the upper whisker to the largest point below the upper quartile +1.5∗IQR, and the lower whisker analogously.

Outliers falling outside the range of the whiskers are then drawn directly:

```{r}
ggplot(gapminder) + geom_boxplot(aes(x = continent, y = gdpPercap))
```
There are variants that distinguish between mild outliers and extreme outliers.

A common variant is to show an approximate 95% confidence interval for the population median as a notch.
```{r}
ggplot(gapminder) +
    geom_boxplot(aes(x = continent, y = gdpPercap), notch = TRUE)
```
Another variant is to use a width proportional to the square root 
of the sample size to reflect the strength of evidence in the data:
```{r}
ggplot(gapminder) +
    geom_boxplot(aes(x = continent, y = gdpPercap),
                 notch = TRUE, varwidth = TRUE)
```
With moderate sample sizes it can be useful to super-impose the original data, perhaps with jittering and alpha blending. The outliers in the box plot can be turned off with ``outlier.color = NA`` so they are not shown twice:

```{r}
p <- ggplot(gapminder) +
    geom_boxplot(aes(x = continent, y = gdpPercap),
                 notch = TRUE, varwidth = TRUE,
                 outlier.color = NA)
p + geom_point(aes(x = continent, y = gdpPercap),
               position = position_jitter(width = 0.1), alpha = 0.1)
```
### Violin Plots
A variant of the boxplot is the violin plot:

*Hintze, J. L., Nelson, R. D. (1998), “Violin Plots: A Box Plot-Density Trace Synergism,” The American Statistician 52, 181-184.*

The violin plot uses density estimates to show the distributions:
```{r}
ggplot(gapminder) + geom_violin(aes(x = continent, y = gdpPercap))
```
By default the “violins” are scaled to have the same area. 
They can also be scaled to have the same maximum height or to have areas proportional to sample sizes. This is done by adding ``scale = "width"`` or  ``scale = "count"`` to the geom_violin call.

A comparison of boxplots and violin plots:
```{r}
ggplot(gapminder) +
    geom_boxplot(aes(x = continent, y = gdpPercap)) +
    geom_violin(aes(x = continent, y = gdpPercap),
                fill = NA, scale = "width", linetype = 2)
```
A Combination of boxplots and violin plots:
```{r}
ggplot(gapminder) +
    geom_violin(aes(x = continent, y = gdpPercap), scale = "width") +
    geom_boxplot(aes(x = continent, y = gdpPercap), width = .1)
```
There are other variations, e.g. vase plots.

## Beeswarm Plots
Beeswarm plots, also called violin scatterplots, try to show both 
the full data and the density of the data distribution.

The ggbeeswarm package provides one implementation with two 
variants:

* ``geom_quasirandom``
* ``geom_beeswarm``

The ``quasi_random`` version seems to work a bit better on many 
examples, e.g.
```{r}
library(ggbeeswarm)
ggplot(gapminder) +
geom_quasirandom(aes(x = continent, y = gdpPercap), size = 0.2)
```
Combined with a width-scaled violin plot:
```{r}
ggplot(gapminder) +
    geom_violin(aes(x = continent, y = gdpPercap), scale = "width") +
    geom_quasirandom(aes(x = continent, y = gdpPercap), color = "blue")
```
### Effectiveness and Scalability
* Boxplots are very simple and easy to compare.
* Boxplots strongly emphasize the middle half of the data.
* Boxplots may not be easy for a lay viewer to understand.
* Box plots scale fairly well visually and computationally in the number of observations; over-plotting/storage of outliers becomes an issue for larger data sets

Violin plots scale well both visually and computationally in the 
number of observations.

```{r}
library(gridExtra)
p1 <- ggplot(diamonds) + geom_boxplot(aes(x = cut, y = price))
p2 <- ggplot(diamonds) + geom_violin(aes(x = cut, y = price))
grid.arrange(p1, p2, nrow = 1)
```
Scalability in the number of cases for beeswarm plots is more limited.

The number of groups that can be handled for comparison by these plots is in the range of a few dozen.
```{r}
library(lattice)
p1 <- ggplot(barley) + geom_boxplot(aes(x = site, y = yield, fill = year))
p2 <- ggplot(barley) + geom_violin(aes(x = site, y = yield, fill = year))
grid.arrange(p1, p2, nrow = 1)
```
### Ridge Plots
Ridgeline plots, also called joy plots, are another way to show 
density estimates for a number of groups that has become popular recently.

The package ggridges defines ``geom_density_ridges`` for creating 
these plots:
```{r}
library(ggridges)
ggplot(barley) + geom_density_ridges(aes(x=yield,y=site,fill = year))
```
## Picking joint bandwidth of 2.39

Alpha blending may sometimes help:

```{r}
ggplot(barley) +
    geom_density_ridges(aes(x=yield,y=site,fill = year), alpha = 0.8)
## Picking joint bandwidth of 2.39
```
Adjusting the vertical scale may also help:
```{r}
ggplot(barley) +
    geom_density_ridges(aes(x=yield,y=site,fill = year), scale = 0.8)
```
## Picking joint bandwidth of 2.39

This work is licensed under the CC BY-NC 3.0 Creative Commons License.
