---
title: "``stat_peaks`` Local maxima (peaks) or minima (valleys)"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggpmisc)
library(dplyr)
library(magrittr)
```



### Description
``stat_peaks`` finds at which x positions local y maxima are located and stat_valleys finds at which x positions local y minima are located. Both stats return x and y numeric values for peaks or
valleys and formatted character labels. The formatting is determined by a format string suitable for ``sprintf()``.

#### Usage 

<pre><code>
stat_peaks(mapping = NULL, data = NULL, geom = "point", span = 5,
ignore_threshold = 0, strict = FALSE, label.fmt = "%.4g",
x.label.fmt = NULL, y.label.fmt = label.fmt, position = "identity",
na.rm = FALSE, show.legend = FALSE, inherit.aes = TRUE, ...)

stat_valleys(mapping = NULL, data = NULL, geom = "point", span = 5,
ignore_threshold = 0, strict = FALSE, label.fmt = "%.4g",
x.label.fmt = NULL, y.label.fmt` = label.fmt, position = "identity",
na.rm = FALSE, show.legend = FALSE, inherit.aes = TRUE, ...)
</code></pre>

### Arguments

* ``mapping``: The aesthetic mapping, usually constructed with ``aes`` or ``aes_``. Only needs to be set at the layer level if you are overriding the plot defaults.
* ``data ``: A layer specific dataset - only needed if you want to override the plot defaults.
* ``geom``: The geometric object to use display the data
* ``span``: a peak is defined as an element in a sequence which is greater than all other elements within a window of width span centered at that element. The default value is 5, meaning that a peak is bigger than two consecutive neighbors on each side. A NULL value for span is taken as a span covering the whole of the data range.
* ``ignore_threshold``: numeric value between 0.0 and 1.0 indicating the size threshold below which peaks will be ignored.
* ``strict``: logical flag: if TRUE, an element must be strictly greater than all other values in its window to be considered a peak. Default: FALSE.
* ``label.fmt`` character string giving a format definition for converting values into character
strings by means of function sprintf.
* ``x.label.fmt`` : character string giving a format definition for converting $x$-values into character
strings by means of function sprintf or strftime.
* ``y.label.fmt`` : character string giving a format definition for converting $y$-values into character
strings by means of function sprintf.
position The position adjustment to use for overlapping points on this layer 
* ``na.rm`` a logical value indicating whether NA values should be stripped before the computation proceeds.
* ``show.legend ``: logical. Should this layer be included in the legends? NA, the default, includes if any aesthetics are mapped. FALSE never includes, and TRUE always includes.
* ``inherit.aes``: If FALSE, overrides the default aesthetics, rather than combining with them.
This is most useful for helper functions that define both data and aesthetics and shouldn't inherit behaviour from the default plot specification, e.g. borders.
* ``...``:   Other arguments passed on to layer. This can include aesthetics whose values
you want to set, not map. See layer for more details..


#### Examples 
```{r}
library(ggplot2)
lynx.df <- data.frame(year = as.numeric(time(lynx)), lynx = as.matrix(lynx))
ggplot(lynx.df, aes(year, lynx)) + geom_line() +
stat_peaks(colour = "red") +
stat_valleys(colour = "blue")
ggplot(lynx.df, aes(year, lynx)) + geom_line() +
stat_peaks(colour = "red") +
stat_peaks(colour = "red", geom = "rug")
```

### Details

These stats use geom_point by default as it is the geom most likely to work well in almost any situation
without need of tweaking. The default aesthetics set by these stats allow their direct use with
``geom_text``, ``geom_label``, ``geom_line``, ``geom_rug``, ``geom_hline`` and ``geom_vline``. 

The formatting of the labels returned can be controlled by the user.


#### Computed variables

* ``x`` x-value at the peak (or valley) as numeric
* ``y`` y-value at the peak (or valley) as numeric
* ``x.label`` x-value at the peak (or valley) as character
* ``y.label`` y-value at the peak (or valley) as character

#### See Also
Other peaks and valleys functions: find_peaks


####  Note
These stats check the scale of the x aesthetic and if is Datetime they correctly generate the labels
by transforming the numeric x values to POSIXct objects, in which case the * ``x.label.fmt`` :
must be suitable for strftime() rather than for sprintf(). These stats work nicely together with geoms geom_text_repel and geom_label_repel from package ggrepel to solve the problem of overlapping labels by displacing them. Alternatively, to discard overlapping labels use check_overlap = TRUE as argument to geom_text. By default the labels are character values suitable to be plotted as is, but with a suitable label.fmt labels suitable for parsing by the geoms (e.g. into expressions containing Greek letters, super- or subscripts, maths symbols or maths constructs) can be also easily obtained.
