
---
title: "``ggpmisc::stat_fit_deviations ``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(ggpmisc)
```


Residuals from model fit as segments

### Description

``stat_fit_deviations`` fits a linear model and returns fitted values and residuals ready to be plotted as segments.

#### Usage 
<pre><code>
stat_fit_deviations(mapping = NULL, data = NULL, geom = "segment",
method = "lm", formula = NULL, position = "identity", na.rm = FALSE,
show.legend = FALSE, inherit.aes = TRUE, ...)
</code></pre>

### Arguments

* ``mapping``: The aesthetic mapping, usually constructed with aes or aes_. Only needs to be set at the layer level if you are overriding the plot defaults.
* ``data ``: A layer specific dataset - only needed if you want to override the plot defaults.
* ``geom`` The geometric object to use display the data
* ``method`` character Currently only "lm" is implemented.
* ``formula`` a "formula" object.
* ``position``: The position adjustment to use for overlapping points on this layer
* ``na.rm``: a logical indicating whether NA values should be stripped before the computation proceeds.
* ``show.legend ``: logical. Should this layer be included in the legends? NA, the default, includes if any aesthetics are mapped. FALSE never includes, and TRUE always includes.
* ``inherit.aes``: If FALSE, overrides the default aesthetics, rather than combining with them. This is most useful for helper functions that define both data and aesthetics and should not inherit behaviour from the default plot specification, e.g. borders.
* ``...``:   Other arguments passed on to layer. This can include aesthetics whose values you want to set, not map. See layer for more details..

### Examples 

```{r} 
library(ggplot2)
# generate artificial data
set.seed(4321)
x <- 1:100
y <- (x + x^2 + x^3) + rnorm(length(x), mean = 0, sd = mean(x^3) / 4)
my.data <- data.frame(x, y, group = c("A", "B"), y2 = y * c(0.5,2))
# give a name to a formula
my.formula <- y ~ poly(x, 3, raw = TRUE)
# plot
ggplot(my.data, aes(x, y)) +
geom_smooth(method = "lm", formula = my.formula) +
stat_fit_deviations(formula = my.formula, color = "red") +
geom_point()
```

### Details
This stat can be used to automatically show residuals as segments in a plot of a fitted model equation. At the moment it supports only linear models fitted with function lm(). This stat only generates the residuals, the predicted values need to be separately added to the plot, so to make sure that the same model formula is used in all steps it is best to save the formula as an object and supply this object as argument to the different statistics.


####Computed variables

Data frame with same nrow as data as subset for each group containing five numeric variables.
x1 x coordinates of observations
x2 x coordinates of fitted values
y1 y coordinates of observations
y2 y coordinates of fitted values
Note
For linear models x1 is equal to x2.
