---
title: "``stat_fit_residuals``:  Residuals from a model fit"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggpmisc)
library(dplyr)
library(magrittr)
```




#### Description
stat_fit_residuals fits a linear model and returns residuals ready to be plotted as points.

#### Usage 

<pre><code>
stat_fit_residuals(mapping = NULL, data = NULL, geom = "point", method = "lm", formula = NULL, resid.type = NULL,
position = "identity", na.rm = FALSE, show.legend = FALSE, inherit.aes = TRUE, ...)
</code></pre>

### Arguments

* ``mapping``: The aesthetic mapping, usually constructed with aes or aes_. Only needs to be
set at the layer level if you are overriding the plot defaults.
* ``data ``: A layer specific dataset - only needed if you want to override the plot defaults.
* geom The geometric object to use display the data method character Currently only "lm" is implemented. 
* formula a "formula" object.
* resid.type character passed to residuals() as argument for type.
* ``position``: The position adjustment to use for overlapping points on this layer
* ``na.rm``: a logical indicating whether NA values should be stripped before the computation proceeds.
* ``show.legend ``: logical. Should this layer be included in the legends? NA, the default, includes if any aesthetics are mapped. FALSE never includes, and TRUE always includes.
* inherit.aes If FALSE, overrides the default aesthetics, rather than combining with them. This is most useful for helper functions that define both data and aesthetics and should not inherit behaviour from the default plot specification, e.g. borders.
* ``...``:   Other arguments passed on to layer. This can include aesthetics whose values
you want to set, not map. See layer for more details..

### Details
This stat can be used to automatically plot residuals as points in a plot. At the moment it supports
only linear models fitted with function lm(). This stat only generates the residuals.

####Computed variables

Data frame with same nrow as data as subset for each group containing five numeric variables.

* x1 x coordinates of observations
* x2 x coordinates of fitted values
* y1 y coordinates of observations
* y2 y coordinates of fitted values
* residuals residuals from the fit

### Examples 

```{r} 
library(ggplot2)
# generate artificial data
set.seed(4321)
x <- 1:100
y <- (x + x^2 + x^3) + rnorm(length(x), mean = 0, sd = mean(x^3) / 4)
my.data <- data.frame(x, y, group = c("A", "B"), y2 = y * c(0.5,2))
# give a name to a formula
my.formula <- y ~ poly(x, 3, raw = TRUE)
# plot
ggplot(my.data, aes(x, y)) +
stat_fit_residuals(formula = my.formula, resid.type = "working")
```
