
stat_dens2d_filter Filter observations by local density
### Description

``stat_dens2d_filter`` Filters out/filters in observations in regions of a plot panel with high density
of observations. stat_dens2d_filter_g does the filtering by group instead of by panel. This
second stat is useful for highlighting observations, while the first one tends to be most useful when
the aim is to prevent clashes among text labels.

#### Usage 
<pre><code>
stat_dens2d_filter(mapping = NULL, data = NULL, geom = "point",
position = "identity", keep.fraction = 0.1, keep.number = Inf,
keep.sparse = TRUE, na.rm = TRUE, show.legend = FALSE,
inherit.aes = TRUE, h = NULL, n = NULL, ...)
stat_dens2d_filter_g(mapping = NULL, data = NULL, geom = "point",
position = "identity", keep.fraction = 0.1, keep.number = Inf,
keep.sparse = TRUE, na.rm = TRUE, show.legend = FALSE,
inherit.aes = TRUE, h = NULL, n = NULL, ...)
</code></pre>


### Arguments

* ``mapping``: The aesthetic mapping, usually constructed with aes or aes_. Only needs to be
set at the layer level if you are overriding the plot defaults.
* ``data ``: A layer specific dataset - only needed if you want to override the plot defaults.
geom The geometric object to use display the data.
* ``position``: The position adjustment to use for overlapping points on this layer
keep.fraction numeric [0..1].
* keep.number integer number of labels to keep.
* keep.sparse logical If false the observations from the densest regions are kept.
* na.rm a logical value indicating whether NA values should be stripped before the computation proceeds.
* ``show.legend ``: logical. Should this layer be included in the legends? NA, the default, includes if
any aesthetics are mapped. FALSE never includes, and TRUE always includes.
* inherit.aes If FALSE, overrides the default aesthetics, rather than combining with them. This is most useful for helper functions that define both data and aesthetics and shouldn’t inherit behaviour from the default plot specification, e.g. borders.
* h vector of bandwidths for x and y directions. Defaults to normal reference bandwidth(see bandwidth.nrd). A scalar value will be taken to apply to both directions.
* n Number of grid points in each direction. Can be scalar or a length-2 integer
vector
* ``...``:   Other arguments passed on to layer. This can include aesthetics whose values
you want to set, not map. See layer for more details..


### Examples 
```{r} 
library(ggrepel)
random_string <- function(len = 6) {
paste(sample(letters, len, replace = TRUE), collapse = "")
}
# Make random data.
set.seed(1001)
d <- tibble::tibble(
x = rnorm(100),
y = rnorm(100),
group = rep(c("A", "B"), c(50, 50)),
lab = replicate(100, { random_string() })
)
```
```{r}
ggplot(data = d, aes(x, y)) +
geom_point() +
stat_dens2d_filter(color = "red")
```
```{r}
ggplot(data = d, aes(x, y)) +
geom_point() +
stat_dens2d_filter(color = "red", keep.fraction = 0.5)
```
```{r}
ggplot(data = d, aes(x, y)) +
geom_point() +
stat_dens2d_filter(color = "red",
keep.fraction = 0.5,
keep.number = 12)
```
```{r}
ggplot(data = d, aes(x, y, color = group)) +
geom_point() +
stat_dens2d_filter(shape = 1, size = 3, keep.fraction = 1/4)
```
```{r}
ggplot(data = d, aes(x, y, color = group)) +
geom_point() +
stat_dens2d_filter_g(shape = 1, size = 3, keep.fraction = 1/4)
```
```{r}
ggplot(data = d, aes(x, y, label = lab, color = group)) +
geom_point() +
stat_dens2d_filter(geom = "text")
```
```{r}
ggplot(data = d, aes(x, y, label = lab, color = group)) +
geom_point() +
stat_dens2d_filter(geom = "text_repel")
```
####Computed variables

labels x at centre of range
See Also
kde2d used internally.
