---
title: "WVplots"
author: "Kevin O Brien"
date: "13 December 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Package 'WVPlots'
November 6, 2018
Type Package
Title Common Plots for Analysis
Version 1.0.6
Date 2018-11-08
URL https://github.com/WinVector/WVPlots,
https://winvector.github.io/WVPlots/
Maintainer John Mount <jmount@win-vector.com>
BugReports https://github.com/WinVector/WVPlots/issues

#### Description
 Select data analysis plots, under a standardized calling interface implemented
on top of 'ggplot2' and 'plotly'.
Plots of interest include: 'ROC', gain curve, scatter plot with marginal distributions,
conditioned scatter plot with marginal densities,
box and stem with matching theoretical distribution, and density with matching theoretical distribution.
License GPL-3
VignetteBuilder knitr
Depends R (>= 3.4.0)
Imports ggplot2 (>= 2.2.0), wrapr (>= 1.6.3), sigr (>= 1.0.3), cdata
(>= 1.0.3), utils, grid, gridExtra, graphics, mgcv
Suggests knitr, testthat, plotly, hexbin
RoxygenNote 6.1.0
ByteCompile true
NeedsCompilation no
Author John Mount [aut, cre],
Nina Zumel [aut],
Win-Vector LLC [cph]
Repository CRAN
Date/Publication 2018-11-06 18:20:03 UTC
1
2 BinaryYScatterPlot
R topics documented:
BinaryYScatterPlot . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 2
ClevelandDotPlot . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 3
ConditionalSmoothedScatterPlot . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 5
DiscreteDistribution . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 6
DoubleDensityPlot . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 6
DoubleHistogramPlot . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 7
GainCurvePlot . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 8
GainCurvePlotC . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 9
GainCurvePlotWithNotation . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 10
HexBinPlot . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 11
LiftCurvePlot . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 12
LogLogPlot . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 13
PairPlot . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 14
PlotDistCountNormal . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 15
PlotDistDensityBeta . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 16
PlotDistDensityNormal . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 17
PlotDistHistBeta . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 17
plotlyROC . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 18
plot_fit_trajectory . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 19
plot_Keras_fit_trajectory . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 21
PRPlot . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 22
ROCPlot . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 23
ROCPlotPair . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 24
ROCPlotPair2 . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 25
ScatterBoxPlot . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 27
ScatterBoxPlotH . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 28
ScatterHist . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 29
ScatterHistC . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 30
ScatterHistN . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 31
ShadedDensity . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 32
ShadedDensityCenter . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 33
ShadowHist . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 34
ShadowPlot . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 35
WVPlots . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 36
Index 37
BinaryYScatterPlot Plot a scatter plot of a binary variable with smoothing curve.

#### Description

Plot the scatter plot of a binary variable with a smoothing curve.

#### Usage

<pre><code>
BinaryYScatterPlot(frame, xvar, yvar, title, ..., se = FALSE,use_glm = TRUE)
</code></pre> 

#### Arguments

* ``frame``: data frame to get values from
* ``xvar ``:  name of the independent column in frame
* ``yvar``:   name of the dependent (output or result to be modeled) column in frame
* ``title ``:    title to place on plot
* ``... `` : no unnamed argument, added to force named binding of later arguments
* ``se``: if TRUE, add error bars (defaults to FALSE). Ignored if useGLM is TRUE
* ``use_glm``: if TRUE, "smooths" with a one-variable logistic regression (defaults to TRUE)

#### Details

The points are jittered for legibility. By default, a logistic regression fit is used, so that the smoothing
curve represents the probability of y == 1 (as fit by the logistic regression). If ``use_glm`` is set to
FALSE, a standard smoothing curve (either loess or a spline fit) is used.
 
#### Examples
```{r}

set.seed(34903490)
x = rnorm(50)
y = 0.5*x^2 + 2*x + rnorm(length(x))
frm = data.frame(x=x,y=y,yC=y>=as.numeric(quantile(y,probs=0.8)))
frm$absY <- abs(frm$y)
frm$posY = frm$y > 0
frm$costX = 1
WVPlots::BinaryYScatterPlot(frm, "x", "posY",
title="Example 'Probability of Y' Plot")
```


ClevelandDotPlot Plot a Cleveland dot plot.

#### Description

Plot counts of a categorical variable.
 
#### Usage
<pre><code>

ClevelandDotPlot(frm, xvar, title, ..., sort = -1, limit_n = NULL,
stem = TRUE)


</code></pre> 
#### Arguments

* ``frm``: data frame to get values from
* ``xvar ``:  name of the independent (input or model) column in frame
* ``title ``:    title to place on plot
* ``... `` : no unnamed argument, added to force named binding of later arguments
* ``sort`` : if TRUE sort data
* ``limit_n`` : if not NULL number of items to plot
* ``stem`` : if TRUE add stems/whiskers to plot

#### Details

Assumes that xvar is a factor or can be coerced to one (character or integral).
* sort < 0 sorts the factor levels in decreasing order (most frequent level first)
* sort > 0 sorts the factor levels in increasing order (good when used in conjunction with coord_
flip())
* sort = 0 leaves the factor levels in "natural order" - usually alphabetical
* stem = FALSE will plot only the dots, without the stem to the y=0 line.
* limit_n = NULL plots all the levels, N an integer limits to the top N most populous levels
 
#### Examples
```{r}

set.seed(34903490)
# discrete variable: letters of the alphabet
# frequencies of letters in English
# source: http://en.algoritmy.net/article/40379/Letter-frequency-English
letterFreqs = c(8.167, 1.492, 2.782, 4.253, 12.702, 2.228,
2.015, 6.094, 6.966, 0.153, 0.772, 4.025, 2.406, 6.749, 7.507, 1.929,
0.095, 5.987, 6.327, 9.056, 2.758, 0.978, 2.360, 0.150, 1.974, 0.074)
letterFreqs = letterFreqs/100
letterFrame = data.frame(letter = letters, freq=letterFreqs)
# now let's generate letters according to their letter frequencies
N = 1000
randomDraws = data.frame(draw=1:N,
letter=sample(letterFrame$letter, size=N,
replace=TRUE, prob=letterFrame$freq))
WVPlots::ClevelandDotPlot(randomDraws, "letter",
title = "Example Cleveland-style dot plot")
# Note the use of sort = 0, and that the graph correctly includes counts
# with no occurrences (5, and 7)
WVPlots::ClevelandDotPlot(mtcars, "carb", sort = 0, "Example of counting integer values")
```

ConditionalSmoothedScatterPlot
Plot a scatter plot with smoothing line.

#### Description

Plot a scatter plot with a smoothing line; the smoothing window is aligned either left, center or
right.
 
#### Usage
<pre><code>

ConditionalSmoothedScatterPlot(frame, xvar, yvar, groupvar, title, ...,
k = 3, align = "center")

</code></pre> 
#### Arguments

* ``frame``: data frame to get values from
* ``xvar ``:  name of the independent column in frame. Assumed to be regularly spaced
* ``yvar``:   name of the dependent (output or result to be modeled) column in frame
groupvar name of the grouping column in frame. Can be NULL for an unconditional plot
* ``title ``:    title for plot
* ``... `` : no unnamed argument, added to force named binding of later 
</code></pre> 
#### Arguments
.
k width of smoothing window. Must be odd for a center-aligned plot. Defaults to
3
align smoothing window alignment: 'center', 'left', or 'right'. Defaults to 'center'

#### Details

xvar is the continuous independent variable and yvar is the dependent binary variable. Smoothing
is by a square window of width k.
 
#### Examples
```{r}

y = c(1,2,3,4,5,10,15,18,20,25)
x = seq_len(length(y))
df = data.frame(x=x, y=y, group=x>5)
WVPlots::ConditionalSmoothedScatterPlot(df, "x", "y", NULL,
title="left smooth, one groups", align="left")
WVPlots::ConditionalSmoothedScatterPlot(df, "x", "y", "group",
title="left smooth, two groups", align="left")
6 DoubleDensityPlot
DiscreteDistribution Plot distribution of a single discrete numerical variable.

#### Description

Similar to calling ClevelandDotPlot with sort = 0 on a numerical x variable that takes on a
discrete set of values.
 
#### Usage
<pre><code>

DiscreteDistribution(frm, xvar, title, ..., stem = TRUE)

</code></pre> 
#### Arguments

* ``frm``: data frame to get values from
xvar numeric: name of the variable whose distribution is to be plotted
* ``title ``:    title to place on plot
* ``... `` : no unnamed argument, added to force named binding of later 
</code></pre> 
#### Arguments
.
stem if TRUE add whisker/stems to plot
 
#### Examples
```{r}

frmx = data.frame(x = rbinom(1000, 20, 0.5))
WVPlots::DiscreteDistribution(frmx, "x","Discrete example")
DoubleDensityPlot Plot two density plots conditioned on an outcome variable.

#### Description

Plot two density plots conditioned on a binary outcome variable.
 
#### Usage
<pre><code>

DoubleDensityPlot(frame, xvar, truthVar, title, ...)

</code></pre> 
#### Arguments

* ``frame``: data frame to get values from
* ``xvar ``:  name of the independent (input or model) column in frame
truthVar name of the dependent (output or result to be modeled) column in frame
* ``title ``:    title to place on plot
* ``... `` : no unnamed argument, added to force named binding of later 
</code></pre> 
#### Arguments
.
DoubleHistogramPlot 7

#### Details

The use case for this visualization is to plot the distribution of a predictive model score (usually the
predicted probability of a desired outcome) conditioned on the actual outcome. However, you can
use it to compare the distribution of any numerical quantity conditioned on a binary feature. See
the  
#### Examples
```{r}
.
The plot will degrade gracefully in degenerate conditions, for example when only one category is
present.
 
#### Examples
```{r}

mpg = ggplot2::mpg
mpg$trans = gsub("\\(.*$", '', mpg$trans)
WVPlots::DoubleDensityPlot(mpg, "cty", "trans", "City driving mpg by transmission type")
set.seed(34903490)
x = rnorm(50)
y = 0.5*x^2 + 2*x + rnorm(length(x))
frm = data.frame(score=x,
truth=(y>=as.numeric(quantile(y,probs=0.8))),
stuck=TRUE,
rare=FALSE)
frm[1,'rare'] = TRUE
WVPlots::DoubleDensityPlot(frm, "score", "truth", title="Example double density plot")
WVPlots::DoubleDensityPlot(frm, "score", "stuck", title="Example double density plot")
WVPlots::DoubleDensityPlot(frm, "score", "rare", title="Example double density plot")









Index
BinaryYScatterPlot, 2
ClevelandDotPlot, 3
ConditionalSmoothedScatterPlot, 5
DiscreteDistribution, 6
DoubleDensityPlot, 6
DoubleHistogramPlot, 7
GainCurvePlot, 8, 10, 11
GainCurvePlotC, 9
GainCurvePlotWithNotation, 10
geom_hex, 12
geom_histogram, 35
HexBinPlot, 11
LiftCurvePlot, 12
LogLogPlot, 13
PairPlot, 14
plot_fit_trajectory, 19, 22
plot_Keras_fit_trajectory, 20, 21
PlotDistCountNormal, 15
PlotDistDensityBeta, 16
PlotDistDensityNormal, 17
PlotDistHistBeta, 17
plotlyROC, 18
PRPlot, 22, 24
ROCPlot, 19, 23, 23, 25, 26
ROCPlotPair, 24
ROCPlotPair2, 25
scale_fill_manual, 35
ScatterBoxPlot, 27, 28
ScatterBoxPlotH, 27, 28
ScatterHist, 29, 31
ScatterHistC, 30, 30, 32
ScatterHistN, 31
ShadedDensity, 32, 34
ShadedDensityCenter, 33, 33
ShadowHist, 34
ShadowPlot, 35
WVPlots, 36
WVPlots-package (WVPlots), 36
37