---
title: "``GainCurvePlotWithNotation``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(WVPlots)
```


#### Description

Plot the cumulative gain curve of a sort-order with extra notation.
 
#### Usage

<pre><code>

GainCurvePlotWithNotation(frame, xvar, truthVar, title, gainx, labelfun,
..., estimate_sig = FALSE, large_count = 1000)

</code></pre> 

#### Arguments

* ``frame``: data frame to get values from
* ``xvar ``:  name of the independent (input or model score) column in frame
* ``truthVar``: name of the dependent (output or result to be modeled) column in frame
* ``title ``:    title to place on plot
* ``gainx``: the point on the x axis corresponding to the desired label
* ``labelfun``: a function to return a label for the marked point
* ``...``: no unarmed argument, added to force named binding of later arguments
* ``estimate_sig``: (logical), if TRUE compute significance
* ``large_count``: (numeric) upper bound target for number of plotting points


 
#### Examples
```{r}

set.seed(34903490)
y = abs(rnorm(20)) + 0.1
x = abs(y + 0.5*rnorm(20))
frm = data.frame(model=x, value=y)
gainx = 0.10 # get the top 10% most valuable points as sorted by the model
# make a function to calculate the label for the annotated point
labelfun = function(gx, gy) {
pctx = gx*100
pcty = gy*100
paste("The top ", pctx, "% most valuable points by the model\n",
"are ", pcty, "% of total actual value", sep='')
}
WVPlots::GainCurvePlotWithNotation(frm, "model", "value",
title="Example Gain Curve with annotation",
gainx=gainx,labelfun=labelfun)
```

#### Details

This is the standard gain curve plot (see GainCurvePlot) with a label attached to a particular value
of x. The label is created by a function labelfun, which takes as inputs the x and y coordinates of
a label and returns a string (the label).
See Also
GainCurvePlot