---
title: "``GainCurvePlotC``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(WVPlots)
```


#### Description

Plot the cumulative gain curve of a sort-order with costs.
 
#### Usage
<pre><code>

GainCurvePlotC(frame, xvar, costVar, truthVar, title, ...,
estimate_sig = FALSE, large_count = 1000)

</code></pre> 




#### Arguments

* ``frame``: data frame to get values from
* ``xvar ``:  name of the independent (input or model score) column in frame
* ``costVar``: cost of each item (drives x-axis sum)
* ``truthVar``: name of the dependent (output or result to be modeled) column in frame
* ``title ``:    title to place on plot
* ``... `` : no unnamed argument, added to force named binding of later arguments
* ``estimate_sig``: (logical), if TRUE compute significance
* ``large_count``: numeric, upper bound target for number of plotting points

#### Examples
```{r}

set.seed(3490)
y = abs(rnorm(20)) + 0.1
x = abs(y + 0.5*rnorm(20))
frm = data.frame(model=x, value=y)
frm$costs=1
frm$costs[1]=5
WVPlots::GainCurvePlotC(frm, "model", "costs", "value",title="Example Continuous Gain CurveC")
```

#### Details

* GainCurvePlotC plots a cumulative gain curve for the case where items have an additional cost, in
addition to an outcome value.

* The x-axis represents the fraction of total cost experienced when items are sorted by score, and the y-axis represents the cumulative summed true outcome represented by the items seen so far.

* For comparison, GainCurvePlotC also plots the "wizard curve": the gain curve when the data is sorted according to its true outcome/cost (the optimal sort order).

* To improve presentation quality, the plot is limited to approximately large_count points (default: 1000). For larger data sets, the data is appropriately randomly sampled down before plotting.

#### See Also
GainCurvePlot
 
