---
title: "``HexBinPlot``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(WVPlots)
```

 

#### Description

Build a hex bin plot with rational color coding.
 
#### Usage

<pre><code>

HexBinPlot(d, xvar, yvar, title, ..., bins = 30, binwidth = NULL,
na.rm = FALSE)

</code></pre> 

#### Arguments

* ``d ``:data frame
* ``xvar ``:  name of x variable column
* ``yvar``: name of y variable column
* ``title``: plot title
* ``...``: not used, forces later arguments to bind by name
* ``bins``: passed to ``geom_hex``
* ``binwidth``: passed to ``geom_hex``
* ``na.rm``: passed to ``geom_hex``


 
#### Examples
```{r}

if(requireNamespace("hexbin", quietly = TRUE)) {
set.seed(634267)
dframe = data.frame(x = rnorm(1000), y = rnorm(1000))
print(HexBinPlot(dframe, "x", "y", "Example hexbin"))
diamonds = ggplot2::diamonds
print(HexBinPlot(diamonds, "carat", "price", "Diamonds example"))
}
```

#### Details

Builds a standard ggplot2 hexbin plot, with a color scale such that dense areas are colored darker
(the default ggplot2 fill scales will color dense areas lighter).
Requires the hexbin package.
Value
a ggplot2 hexbin plot
See Also
geom_hex