---
title: "``LiftCurvePlot``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(WVPlots)
```




#### Description

Plot the cumulative lift curve of a sort-order.

 
#### Usage
<pre><code>

LiftCurvePlot(frame, xvar, truthVar, title, ..., large_count = 1000,
include_wizard = TRUE)

</code></pre> 
#### Arguments

* ``frame``: data frame to get values from
* ``xvar ``:  name of the independent (input or model score) column in frame
* ``truthVar``: name of the dependent (output or result to be modeled) column in frame
* ``title ``:    title to place on plot
* ``... `` : no unnamed argument, added to force named binding of later arguments
* ``large_count`` : numeric, upper bound target for number of plotting points
* ``include_wizard`` : (logical) if TRUE plot the ideal or wizard plot.


 
#### Examples
```{r}

set.seed(34903490)
y = abs(rnorm(20)) + 0.1
x = abs(y + 0.5*rnorm(20))
frm = data.frame(model=x, value=y)
WVPlots::LiftCurvePlot(frm, "model", "value",
title="Example Continuous Lift Curve")
```

#### Details

* The use case for this visualization is to compare a predictive model score to an actual outcome (either binary (0/1) or continuous). In this case the lift curve plot measures how well the model score sorts the data compared to the true outcome value.
* The x-axis represents the fraction of items seen when sorted by score, and the y-axis represents the lift seen so far (cummulative value of model over cummulative value of random selection).
* For comparison, LiftCurvePlot also plots the "wizard curve": the lift curve when the data is sorted
according to its true outcome.
* To improve presentation quality, the plot is limited to approximately large_count points (default: 1000). For larger data sets, the data is appropriately randomly sampled down before plotting.