---
title: "``plot_fit_trajectory``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(WVPlots)
```

#### Description

Plot a history of model fit performance over the a trajectory of times.
 
#### Usage
<pre><code>
plot_fit_trajectory(d, column_description, title, ..., epoch_name = "epoch", needs_flip = c(), pick_metric = NULL,
discount_rate = NULL, draw_ribbon = FALSE, draw_segments = FALSE)
</code></pre> 

#### Arguments

* ``	d 	``:	data frame to get values from.
* ``	column_description	``:	Description  of column measures (data.frame with columns measure, validation, and training).
* ``	title 	``:	character title for plot.
* ``	... 	``:	force later arguments to be bound by name
* ``	epoch_name 	``:	name for epoch or trajectory column.
* ``	needs_flip 	``:	character array of measures that need to be flipped.
* ``	pick_metric	``:	character metric to maximize.
* ``	discount_rate 	``:	numeric what fraction of over-fit to subtract from validation performance.
* ``	draw_ribbon 	``:	present the difference in training and validation performance as a ribbon rather than two curves? (default FALSE)
* ``	draw_segments	``:	logical if TRUE draw over-fit/under-fit segments.


 
#### Examples
```{r}

d <- data.frame(
  epoch = c(1, 2, 3, 4, 5),
  val_loss = c(0.3769818, 0.2996994, 0.2963943, 0.2779052, 0.2842501),
  val_acc = c(0.8722000, 0.8895000, 0.8822000, 0.8899000, 0.8861000),
  loss = c(0.5067290, 0.3002033, 0.2165675, 0.1738829, 0.1410933),
  acc = c(0.7852000, 0.9040000, 0.9303333, 0.9428000, 0.9545333) )

cT <- data.frame(
measure = c("minus binary cross entropy", "accuracy"),
training = c("loss", "acc"),
validation = c("val_loss", "val_acc"),
stringsAsFactors = FALSE)
```
```{r}
plt <- plot_fit_trajectory(
d,
column_description = cT,
needs_flip = "minus binary cross entropy",
title = "model performance by epoch, dataset, and measure",
epoch_name = "epoch")
```

```{r}
plt
```

```{r}
plt <- plot_fit_trajectory(
d,
column_description = cT,
needs_flip = "minus binary cross entropy",
title = "model performance by epoch, dataset, and measure",
epoch_name = "epoch",
pick_metric = "minus binary cross entropy",
discount_rate = 0.1)
suppressWarnings(print(plt)) # too few points for loess
```

#### Details

This visualization can be applied to any staged machine learning algorithm. For example one could
plot the performance of a gradient boosting machine as a function of the number of trees added.
The fit history data should be in the form given in the example below.
The example below gives a fit plot for a history report from Keras R package. Please see http://
www.win-vector.com/blog/2017/12/plotting-deep-learning-model-performance-trajectories/
for some examples and details

Value
ggplot2 plot
See Also
plot_Keras_fit_trajectory