---
title: "``plotlyROC``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(WVPlots)
library(plotly)
```


#### Description

Use plotly to produce a ROC plot.
 
#### Usage

<pre><code>
plotlyROC(d, predCol, outcomeCol, outcomeTarget, title, ...,
estimate_sig = FALSE)
</code></pre> 

#### Arguments

* ``d``: dataframe
* ``predCol``:  name of column with numeric predictions
* ``outcomeCol``: name of column with truth
* ``outcomeTarget``: value considered true
* ``title``: character title for plot
* ``... `` : no unnamed argument, added to force named binding of later arguments
* ``estimate_sig``: (logical), if TRUE estimate and display significance of difference from AUC 0.5.

 
#### Examples
```{r}

if(requireNamespace("plotly", quietly = TRUE)) {
set.seed(34903490)
x = rnorm(50)
y = 0.5*x^2 + 2*x + rnorm(length(x))
frm = data.frame(x=x,yC=y>=as.numeric(quantile(y,probs=0.8)))
plotlyROC(frm, 'x', 'yC', TRUE, 'example plot', estimate_sig = TRUE)
}
```

#### Value
plotly plot

#### See Also
ROCPlot