---
title: "``ScatterHist``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(WVPlots)
```

Plot a scatter plot with marginals.

#### Description

* Plot a scatter plot with optional smoothing curves or contour lines, and marginal histogram/density plots. 
* Based on http://www.win-vector.com/blog/2015/06/wanted-a-perfect-scatterplot-with-marginals/.
* See also ggExtra::ggMarginal.
 
#### Usage
<pre><code>

ScatterHist(frame, xvar, yvar, title, ..., smoothmethod = "lm",
estimate_sig = FALSE, minimal_labels = TRUE, binwidth_x = NULL,
binwidth_y = NULL, adjust_x = 1, adjust_y = 1, point_alpha = 0.5,
contour = FALSE)

</code></pre> 
#### Arguments

* ``frame``: data frame to get values from
* ``xvar ``:  name of the independent (input or model) column in frame
* ``yvar``:   name of the dependent (output or result to be modeled) column in frame
* ``title ``:    title to place on plot
* ``... `` : no unnamed argument, added to force named binding of later arguments
* ``smoothmethod ``: (optional) one of 'auto', 'loess', 'gam', 'lm', or 'identity'.
* ``estimate_sig``: (logical) if TRUE and smoothmethod is 'identity' or 'lm', report goodness of fit
and significance of relation.
* ``minimal_labels``: logical drop some annotations
* ``binwidth_x``: numeric binwidth for x histogram
* ``binwidth_y``: numeric binwidth for y histogram
* ``adjust_x``: numeric adjust x density plot
* ``adjust_y``: numeric adjust y density plot
* ``point_alpha``: numeric opaqueness of the plot points
* ``contour``: logical if TRUE add a 2d contour plot


 
#### Examples
```{r}

set.seed(34903490)
x = rnorm(50)
y = 0.5*x^2 + 2*x + rnorm(length(x))
frm = data.frame(x=x,y=y)
WVPlots::ScatterHist(frm, "x", "y",
title= "Example Fit",
smoothmethod = "gam",
contour = TRUE)
```

#### Details

If ``smoothmethod`` is: 'auto', 'loess' or 'gam': the appropriate smoothing curve is added to the scatterplot.
* 'lm' (the default): the best fit line is added to the scatterplot.
* 'identity': the line x = y is added to the scatterplot. This is useful for comparing model
predictions to true outcome.
* 'none': no smoothing line is added to the scatterplot.

If ``estimate_sig`` is TRUE and smoothmethod is:

* 'lm': the R-squared of the linear fit is reported.
* 'identity': the R-squared of the exact relation between xvar and yvar is reported.

Note that the identity R-squared is NOT the square of the correlation between xvar and yvar (which
includes an implicit shift and scale). It is the coefficient of determination between xvar and yvar,
and can be negative. See https://en.wikipedia.org/wiki/Coefficient_of_determination
for more details. 

If xvar is the output of a model to predict yvar, then the identity R-squared, not the lm R-squared, is the correct measure.
If smoothmethod is neither 'lm' or 'identity' then estimate_sig is ignored.

#### Value

plot grid

#### See Also

ScatterHistC