---
title: "``ScatterHistN``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(WVPlots)
```
Plot a height scatter plot with marginals.

#### Description

Plot a scatter plot conditioned on a continuous variable, with marginal conditional density plots.
 
#### Usage
<pre><code>

ScatterHistN(frame, xvar, yvar, zvar, title, ..., annot_size = 3,
colorPalette = "RdYlBu", nclus = 3, adjust_x = 1, adjust_y = 1)

</code></pre> 

#### Arguments

* ``frame``: data frame to get values from
* ``xvar ``:  name of the x variable
* ``yvar``:   name of the y variable
* ``zvar``:   name of height variable
* ``title ``:    title to place on plot
* ``... `` : no unnamed argument, added to force named binding of later arguments
* ``annot_size ``: (numeric) scale annotation text (if present)
* ``colorPalette``: name of a Brewer palette (see http://colorbrewer2.org/ )
* ``nclus scalar``: number of z-clusters to plot
* ``adjust_x ``: (numeric) adjust x density plot
* ``adjust_y ``: (numeric) adjust y density plot


#### Examples
```{r}

set.seed(34903490)
frm = data.frame(x=rnorm(50),y=rnorm(50))
frm$z <- frm$x+frm$y
WVPlots::ScatterHistN(frm, "x", "y", "z", title="Example Joint Distribution")
```
#### Details

xvar and yvar are the coordinates of the points, and zvar is the continuous conditioning variable.
zvar is partitioned into nclus disjoint ranges (by default, 3), which are then treated as discrete
categories.The scatterplot and marginal density plots are color-coded by these categories.

#### See Also
ScatterHistC