---
title: "``ScatterHistC``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(WVPlots)
```

Plot a conditional scatter plot with marginals.

#### Description

Plot a scatter plot conditioned on a discrete variable, with marginal conditional density plots.
 
#### Usage
<pre><code>

ScatterHistC(frame, xvar, yvar, cvar, title, ..., annot_size = 3,
colorPalette = "Dark2", adjust_x = 1, adjust_y = 1)


</code></pre> 
#### Arguments

* ``frame``: data frame to get values from
* ``xvar ``:  name of the x variable
* ``yvar``:  name of the y variable
* ``cvar``: name of condition variable
* ``title ``:    title to place on plot
* ``... `` : no unnamed argument, added to force named binding of later arguments

* ``annot_size`` : (numeric) scale annotation text (if present)
* ``colorPalette`` : name of a Brewer palette (see http://colorbrewer2.org/ )
* ``adjust_x`` : (numeric) adjust x density plot
* ``adjust_y`` : (numeric) adjust y density plot


#### Examples
```{r}

set.seed(34903490)
frm = data.frame(x=rnorm(50),y=rnorm(50))
frm$cat <- frm$x+frm$y>0
WVPlots::ScatterHistC(frm, "x", "y", "cat",
title="Example Conditional Distribution")

```

#### Details

xvar and yvar are the coordinates of the points, and cvar is the discrete conditioning variable that
indicates which category each point (x,y) belongs to.

#### Value
plot grid

#### See Also
ScatterHist
 