---
title: "``ScatterBoxPlot``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(WVPlots)
```

#### Description

Plot a boxplot with the data points superimposed.
 
#### Usage

<pre><code>

ScatterBoxPlot(frm, xvar, yvar, title, ..., pt_alpha = 0.3)

</code></pre> 

#### Arguments

* ``frm``: data frame to get values from
* ``xvar ``:  name of the independent column in frame; assumed discrete
* ``yvar``:   name of the continuous column in frame title plot title
* ``...``: (doesn't take additional arguments, used to force later arguments by name)
* ``pt_alpha``: transparency of points in scatter plot



#### Examples

```{r}

classes = c("a", "b", "c")
means = c(2, 4, 3)
names(means) = classes
label = sample(classes, size=1000, replace=TRUE)
meas = means[label] + rnorm(1000)
frm2 = data.frame(label=label,
meas = meas)

WVPlots::ScatterBoxPlot(frm2, "label", "meas", pt_alpha=0.2, title="Example Scatter/Box plot")
```

#### Details

xvar is a discrete variable and yvar is a continuous variable. If frm[[xvar]] is an integer column,
it will be converted to a factor. This means that additional layers that rely on continuous x scales
(like geom_smooth) won't work.
See Also
ScatterBoxPlotH