---
title: "``ShadowPlot`` Plot a Shadow Bar Plot"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(WVPlots)
```


#### Description

Plot a bar chart of row counts conditioned on the categorical variable condvar, faceted on a second categorical variable, refinevar. Each faceted plot also shows a "shadow plot" of the totals conditioned on condvar alone.
 
#### Usage
<pre><code>

ShadowPlot(frm, condvar, refinevar, title, ..., ncol = 1)


</code></pre> 
#### Arguments

* ``frm``: data frame to get values from.
* ``condvar ``:   name of the primary conditioning variable (a categorical variable, controls xaxis).
* ``refinevar``: name of the second or refining conditioning variable (also a categorical variable,
controls faceting).
* ``title ``:    title to place on plot.
* ``... `` : no unnamed argument, added to force named binding of later arguments
* ``ncol``:  (numeric): number of columns in facet_wrap.
 -  Examples:  grouped by condvar, faceted by refinevar.
 
#### Examples
```{r}

ShadowPlot(mtcars, "carb", "cyl",
title = "Number of example cars by carb and cyl counts")
```

#### Details

This plot enables comparisons of subpopulation totals across both condvar and refinevar simultaneously.
By default, the facet plots are arranged in a single column. This can be changed with the optional
ncol argument.
Please see here for some interesting discussion https://drsimonj.svbtle.com/plotting-background-data-for-groups-Value
a ggplot2 bar chart counting  