---
title: "``ShadedDensity``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(WVPlots)
```

 Plot the distribution of a variable with a tail shaded

#### Description

Plot the distribution of a variable with a tail shaded. Annotate with the area of the shaded region.
 
#### Usage
<pre><code>

ShadedDensity(frame, xvar, threshold, title, ..., tail = "left",
linecolor = "darkgray", shading = "darkblue", annotate_area = TRUE)


</code></pre> 
#### Arguments

* ``frame``: data frame to get values from
* ``xvar ``:  name of the variable to be density plotted
* ``threshold``: boundary value for the tail
* ``title ``:    title to place on plot
* ```...`` : no unnamed argument, added to force named binding of later arguments
* ``tail``:    which tail to shade, 'left' (default) or 'right'
* ``linecolor``:   color of density curve
* ``shading``:  color of shaded region and boundaries
* ``annotate_area``: if TRUE (default), report the area of the shaded region

#### Examples
```{r}

set.seed(52523)
d = data.frame(meas=rnorm(100))
threshold = -1.5
WVPlots::ShadedDensity(d, "meas", threshold,
title="Example shaded density plot, left tail")
```

```{r}
WVPlots::ShadedDensity(d, "meas", -threshold, tail="right",
title="Example shaded density plot, right tail")
```
See Also
ShadedDensityCenter
 
 