---
title: "``ShadedDensityCenter``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(WVPlots)
```

 
#### Description

* Plot the distribution of a variable with a center region shaded. 
* Annotate with the area of the shaded region.
 
#### Usage
<pre><code>

ShadedDensityCenter(frame, xvar, boundaries, title, ...,
linecolor = "darkgray", shading = "darkblue", annotate_area = TRUE)

</code></pre> 

#### Arguments

* ``frame``: data frame to get values from
* ``xvar ``:  name of the variable to be density plotted boundaries vector of the min and max boundaries of the shaded region
* ``title ``:    title to place on plot
* ``... `` : no unnamed argument, added to force named binding of later arguments
* ``linecolor``:   color of density curve
* ``shading``:  color of shaded region and boundaries
* ``annotate_area``: if TRUE (default), report the area of the shaded region

 
#### Examples
```{r}

set.seed(52523)
d = data.frame(meas=rnorm(100))
boundaries = c(-1.5, 1.5)
WVPlots::ShadedDensityCenter(d, "meas", boundaries,
title="Example center-shaded density plot")
```

#### See Also
ShadedDensity
