---
title: "``ShadowHist`` Plot a Shadow Histogram Plot"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(WVPlots)
```

#### Description

* Plot a histogram of a continuous variable xvar, faceted on a categorical conditioning variable,
***condvar***. 
* Each faceted plot also shows a "shadow plot" of the unconditioned histogram for comparison.
 
#### Usage

<pre><code>

ShadowHist(frm, xvar, condvar, title, ..., ncol = 1, palette = "Dark2",
bins = 30, binwidth = NULL)

</code></pre> 

#### Arguments

* ``frm``: data frame to get values from.
* ``xvar ``:  name of the primary continuous variable
* ``condvar ``:   name of conditioning variable (categorical variable, controls faceting).
* ``title ``:    title to place on plot.
* ``... `` : no unnamed argument, added to force named binding of later arguments
* ``ncol``:  (numeric): number of columns in facet_wrap.
* ``palette``:  (character): name of brewer color palette (can be NULL)
* ``bins``: number of bins. Defaults to thirty.
* ``binwidth``: width of the bins. Overrides bins.


 
#### Examples

```{r}

ShadowHist(iris, "Petal.Length", "Species",
title = "Petal Length distribution by Species")
```

#### Details

* Currently supports only the bins and binwidth arguments (see geom_histogram), but not the
center, boundary, or breaks arguments
* By default, the facet plots are arranged in a single column. This can be changed with the optional
ncol argument.
* If palette is NULL, plot colors will be chosen from the default ggplot2 palette. Setting palette
to NULL allows the user to choose a non-Brewer palette, for example with scale_fill_manual.
* Please see here for some interesting discussion https://drsimonj.svbtle.com/plotting-background-data-for-groups-Value
a ggplot2 histogram plot