---
title: "hc_add_series_labels_values"
author: "Kevin O'Brien"
date: "12 October 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(highcharter)
library(dplyr)
library(magrittr)

```
Shorcut for add series for pie, bar and column charts

#### Description 

This function add data to plot pie, bar and column charts.

#### Usage
<pre><code>
hc_add_series_labels_values(hc, labels, values, colors = NULL, ...)
</code></pre>
#### Arguments 

* ``hc ``: A highchart htmlwidget object.
* ``labels``: A vector of labels.
* ``values``: A numeric vector. Same length of labels.
* ``colors``: A not required color vector (hexadecimal format). Same length of labels.
* ``...``: Aditional shared arguments for the data series 
(http://api.highcharts.com/highcharts#series).

####Examples
```{r}

data("favorite_bars")
data("favorite_pies")
highchart() %>%
hc_title(text = "This is a bar graph describing my favorite pies
including a pie chart describing my favorite bars") %>%
hc_subtitle(text = "In percentage of tastiness and awesomeness") %>%
hc_add_series_labels_values(favorite_pies$pie, favorite_pies$percent, name = "Pie",
colorByPoint = TRUE, type = "column") %>%
hc_add_series_labels_values(favorite_bars$bar, favorite_bars$percent,
colors = substr(terrain.colors(5), 0 , 7), type = "pie",
name = "Bar", colorByPoint = TRUE, center = c('35%', '10%'),
size = 100, dataLabels = list(enabled = FALSE)) %>%
hc_yAxis(title = list(text = "percentage of tastiness"),
labels = list(format = "{value}%"), max = 100) %>%
hc_xAxis(categories = favorite_pies$pie) %>%
hc_legend(enabled = FALSE) %>%
hc_tooltip(pointFormat = "{point.y}%")
```