---
title: "hc_add_series_flags"
author: "KevinO'Brien"
date: "11 October 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(highcharter)
library(dplyr)
library(magrittr)
library(treemap)
library(quantmod)
```
hc_add_series_flags
Shorcut for add flags to highstock chart

#### Description 

This function helps to add flags highstock charts created from xts objects.

#### Usage
<pre><code>
hc_add_series_flags(hc, dates, title = LETTERS[seq(length(dates))],
text = title, id = NULL, ...)
</code></pre>

#### Arguments 

* ``hc ``: A highchart htmlwidget object.
* ``dates``: Date vector.
* ``title``: A character vector with titles.
* ``text``: A character vector with the description.
* ``id``: The name of the series to add the flags. A previous series must be added whith
this id.
* ``...``: Additional shared arguments for the *flags* data series 
(http://api.highcharts.com/highstock#plotOptions.flags)

#### Examples
```{r}
library("quantmod")
usdjpy <- getSymbols("USD/JPY", src="oanda", auto.assign = FALSE)
dates <- as.Date(c("2015-05-08", "2015-09-12"), format = "%Y-%m-%d")
highchart(type = "stock") %>%
hc_add_series_xts(usdjpy, id = "usdjpy") %>%
hc_add_series_flags(dates,
title = c("E1", "E2"),
text = c("This is event 1", "This is the event 2"),
id = "usdjpy")
```






