---
title: "hc_add_series_scatter"
author: "KevinO'Brien"
date: "12 October 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(highcharter)
library(dplyr)
library(magrittr)
```


#### Description 

This function helps to create scatter plot from two numerics vectors. Options argumets like size,
color and label for points are added.

#### Usage
<pre><code>
hc_add_series_scatter(hc, x, y, z = NULL, color = NULL, label = NULL,
showInLegend = FALSE, ...)
</code></pre>
#### Arguments 

* ``hc ``: A highchart htmlwidget object.
x A numeric vector.
y A numeric vector. Same length of x.
z A numeric vector for size. Same length of x.
color A vector to color the points.
label A vector to put names in the dots if you enable the datalabels.
showInLegend Logical value to show or not the data in the legend box.
* ``...``: Aditional shared arguments for the data series (http://api.highcharts.com/
highcharts#series).
#### Examples
```{r}

hc <- highchart()
hc_add_series_scatter(hc,mtcars$wt,mtcars$mpg)
```

```{r}
hc_add_series_scatter(hc,mtcars$wt,mtcars$mpg, mtcars$drat)
```

```{r}hc_add_series_scatter(hc,mtcars$wt,mtcars$mpg, mtcars$drat, mtcars$am)
```

```{r}
hc_add_series_scatter(hc,mtcars$wt,mtcars$mpg, mtcars$drat, mtcars$qsec)
hc_add_series_scatter(hc,mtcars$wt,mtcars$mpg, mtcars$drat, mtcars$qsec, rownames(mtcars))



```

```{r}


# Add named attributes to data (attributes length needs to match number of rows)
hc_add_series_scatter(hc, mtcars$wt, mtcars$mpg, mtcars$drat, mtcars$qsec,
name = rownames(mtcars), gear = mtcars$gear) %>%
hc_tooltip(pointFormat = "<b>{point.name}</b><br/>Gear: {point.gear}")
## End(Not run)
```

