---
title: "hc_add_series_map"
author: "KevinO'Brien"
date: "11 October 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(highcharter)
library(dplyr)
library(magrittr)
library(treemap)
```

## ``hc_add_series_map``

Add a map series

#### Description 

Add a map series
Usage
hc_add_series_map(hc, map, df, value, joinBy, ...)

#### Arguments 

* ``hc ``: A highchart htmlwidget object.
* map A list object loaded from a geojson file.
* df A data.frame object with data to chart. Code region and value are required.
* value A string value with the name of the column to chart.
* joinBy What property to join the map and df
* ... Aditional shared arguments for the data series (http://api.highcharts.com/highcharts#series).

#### Details
This function force the highchart object to be map type.

####Examples
```{r}

library("dplyr")
data("USArrests", package = "datasets")
data("usgeojson")
USArrests <- mutate(USArrests, state = rownames(USArrests))
highchart() %>%
hc_title(text = "Violent Crime Rates by US State") %>%
hc_subtitle(text = "Source: USArrests data") %>%
hc_add_series_map(usgeojson, USArrests, name = "Murder arrests (per 100,000)",
value = "Murder", joinBy = c("woename", "state"),
dataLabels = list(enabled = TRUE,format = '{point.properties.postalcode}')) %>%
hc_colorAxis(stops = color_stops()) %>%
hc_legend(valueDecimals = 0, valueSuffix = "%") %>%
hc_mapNavigation(enabled = TRUE)
## Not run:32
hc_add_series_ohlc
data(worldgeojson, package = "highcharter")
data("GNI2014", package = "treemap")
highchart(type = "map") %>%
hc_add_series_map(map = worldgeojson, df = GNI2014, value = "GNI", joinBy = "iso3") %>%
hc_colorAxis(stops = color_stops()) %>%
hc_tooltip(useHTML = TRUE, headerFormat = "",
pointFormat = "this is {point.name} and have {point.population} people with gni of {point.GNI}")
## End(Not run)
```
