---
title: "hcmap: Shorcut for create map"
author: "Kevin O'Brien"
date: "12 October 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Shorcut for create map from https://code.highcharts.com/mapdata/ collection.

#### Description 

Shorcut for create map Shorcut for create map from https://code.highcharts.com/mapdata/
collection.

#### Usage
<pre><code>
hcmap(map = "custom/world",
download_map_data = getOption("highcharter.download_map_data"),
data = NULL, value = NULL, joinBy = NULL, ...)
</code></pre>

#### Arguments 

* map String indicating what map to chart.
* download_map_data A logical value whether to download (add as a depedeny) the map. Default is FALSE.
* data Optional data to make a choropleth, in case of use the joinBy and value are
needed.
* value A string value with the name of the column to chart.
* joinBy What property to join the map and df. the map.
* ... Aditional shared arguments for the data series (http://api.highcharts.com/highcharts#series).

#### Examples
```{r}

require(dplyr)
hcmap(nullColor = "#DADADA")
hcmap(nullColor = "#DADADA", download_map_data = TRUE)
data("USArrests", package = "datasets")
USArrests <- mutate(USArrests, "woe-name" = rownames(USArrests))
hcmap(map = "countries/us/us-all", data = USArrests,
joinBy = "woe-name", value = "UrbanPop", name = "Urban Population")
hcmap(map = "countries/us/us-all", data = USArrests,
joinBy = "woe-name", value = "UrbanPop", name = "Urban Population",
download_map_data = TRUE)
```