
```{r}
# Upload ologit.csv
```
3 Ordinal Logistic ologit.csv

```{r}
ggplot(dat, aes(x = apply, y = gpa)) +
  geom_boxplot(size = .75) +
  geom_jitter(alpha = .5) +
  facet_grid(pared ~ public, margins = TRUE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))
```

```{r}
newdat <- data.frame(
  pared = rep(0:1, 200),
  public = rep(0:1, each = 200),
  gpa = rep(seq(from = 1.9, to = 4, length.out = 100), 4))
```

```{r}
newdat <- cbind(newdat, predict(m, newdat, type = "probs"))
```
Now we can reshape the data long with the reshape2 package and plot all of the predicted probabilities for the different conditions. 
We plot the predicted probilities, connected with a line, coloured by level of the outcome, apply, and facetted by level of pared and public. We also use a custom label function, to add clearer labels showing what each column and row of the plot represent.

```{r}

lnewdat <- melt(newdat, id.vars = c("pared", "public", "gpa"),
  variable.name = "Level", value.name="Probability")
```
```{r}

ggplot(lnewdat, aes(x = gpa, y = Probability, colour = Level)) +
  geom_line() +
  facet_grid(pared ~ public, scales="free",
    labeller=function(x, y) sprintf("%s = %d", x, y))
```
