Installation
To install Plotly's python package, use the package manager pip inside your terminal.
If you don't have pip installed on your machine, click here for pip's installation instructions. 

\begin{framed}
\begin{verbatim}
$ pip install plotly 
or 
$ sudo pip install plotly 

Plotly's Python package is updated frequently! To upgrade, run: 

$ pip install plotly --upgrade
\end{verbatim}
\end{framed}
\end{frame}
%===========================================================%

%===========================================================%
Initialization for Online Plotting
Plotly provides a web-service for hosting graphs! 
Create a free account to get started. 
Graphs are saved inside your online Plotly account and you control the privacy. 
Public hosting is free, for private hosting, check out our paid plans. 

After installing the Plotly package, you're ready to fire up python: 

%=======================%
\begin{frame}[fragile]
\large
\texttt{Accessing Your Account}
\begin{framed}
\begin{verbatim}

import plotly 

plotly.tools.set_credentials_file(
	username='DemoAccount', 
	api_key='lr1c37zw81')

\end{verbatim}
\end{framed}
Find your API key on your account page.
\end{frame}
%=======================%
You'll need to replace 'DemoAccount' and 'lr1c37zw81' with your Plotly username 
and API key.


The initialization step places a special .plotly/.credentials file 
in your home directory. 
Your ~/.plotly/.credentials file should look something like this: 
{
    "username": "DemoAccount",
    "stream_ids": ["ylosqsyet5", "h2ct8btk1s", "oxz4fm883b"],
    "api_key": "lr1c37zw81"
}
\end{verbatim}
\end{framed}

%=======================%
