1. Logistic Regression
2. Multinomial Logistic Regression
3. Ordinal Logistic Regression
4. Poisson Regression
5. Negative Binomial Models
6. Zero - Inflated Poisson Models
7. Zero - Inflated Negative Binomial Models
8. Tobit Regression
9. Truncated Regression
10. Interval Regression

<!-------------------------------------------------------------------->

#### 1. Logistic Regression
A researcher is interested in how variables, such as ***GRE*** (Graduate Record Exam scores), ***GPA*** (grade point average) and prestige of the undergraduate institution, effect admission into graduate school. The response variable, ***admit/don't admit***, is a binary variable.

This dataset has a binary response (outcome, dependent) variable called ***admit***. There are three predictor variables: ***gre***, ***gpa*** and ***rank***. We will treat the variables gre and gpa as continuous. The variable rank takes on the values 1 through 4. Institutions with a rank of 1 have the highest prestige, while those with a rank of 4 have the lowest. We can get basic descriptives for the entire data set by using `summary`. 

To get the standard deviations, we use sapply to apply the sd function to each variable in the dataset.
```{r}
summary(newdata3)

```

```{r}
ggplot(newdata3, aes(x = gre, y = PredictedProb)) +
  geom_ribbon(aes(ymin = LL, ymax = UL, fill = rank), alpha = .2) +
  geom_line(aes(colour = rank), size=1)
```

```{r}
## melt data set to long for ggplot2
lpp <- melt(pp.write, id.vars = c("ses", "write"), value.name = "probability")
head(lpp) # view first few rows
```

```{r}
ggplot(lpp, aes(x = write, y = probability, colour = ses)) +
  geom_line() +
  facet_grid(variable ~ ., scales="free")
```
<!------------------------------------------------------------->


#### 2. Multinomial Logistic Regression

Entering high school students make program choices among general program, vocational program and academic program. Their choice might be modeled using their writing score and their social economic status.

```{r}
## plot predicted probabilities across write values for
## each level of ses facetted by program type

ggplot(lpp, aes(x = write, y = probability, colour = ses)) +
  geom_line() +
  facet_grid(variable ~ ., scales="free")
```

<!------------------------------------------------------------->


#### 3. Ordinal Logistic Regression

A study looks at factors that influence the decision of whether to apply to graduate school. College juniors are asked if they are unlikely, somewhat likely, or very likely to apply to graduate school. Hence, our outcome variable has three categories. Data on parental educational status, whether the undergraduate institution is public or private, and current GPA is also collected. The researchers have reason to believe that the "distances" between these three points are not equal. For example, the "distance" between "unlikely" and "somewhat likely" may be shorter than the distance between "somewhat likely" and "very likely".

```{r}
ggplot(dat, aes(x = apply, y = gpa)) +
  geom_boxplot(size = .75) +
  geom_jitter(alpha = .5) +
  facet_grid(pared ~ public, margins = TRUE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))
```
```{r}
lnewdat <- melt(newdat, id.vars = c("pared", "public", "gpa"),
  variable.name = "Level", value.name="Probability")
## view first few rows
```
```{r}
head(lnewdat)
##   pared public   gpa    Level Probability
## 1     0      0 1.900 unlikely      0.7376
## 2     1      0 1.921 unlikely      0.4932
## 3     0      0 1.942 unlikely      0.7325
## 4     1      0 1.964 unlikely      0.4867
## 5     0      0 1.985 unlikely      0.7274
## 6     1      0 2.006 unlikely      0.4802
```
```{r}
ggplot(lnewdat, aes(x = gpa, y = Probability, colour = Level)) +
  geom_line() +
  facet_grid(pared ~ public, scales="free",
    labeller=function(x, y) sprintf("%s = %d", x, y))
```
<!------------------------------------------------------------->
#### 4. Poisson Regression

In this example, `num_awards` is the outcome variable and indicates the number of awards earned by students at a high school in a year, math is a continuous predictor variable and represents students' scores on their math final exam, and prog is a categorical predictor variable with three levels indicating the type of program in which the students were enrolled. It is coded as 1 = "General", 2 = "Academic" and 3 = "Vocational". 

```{r}
ggplot(p, aes(num_awards, fill = prog)) +
  geom_histogram(binwidth=.5, position="dodge")
```
```{r}
## calculate and store predicted values
p$phat <- predict(m1, type="response")

## order by program and then by math
p <- p[with(p, order(prog, math)), ]

## create the plot
ggplot(p, aes(x = math, y = phat, colour = prog)) +
  geom_point(aes(y = num_awards), alpha=.5, position=position_jitter(h=.2)) +
  geom_line(size = 1) +
  labs(x = "Math Score", y = "Expected number of awards")
  
```
<!------------------------------------------------------------->
#### 5. Negative Binomial Models

School administrators study the attendance behavior of high school juniors at two schools. Predictors of the number of days of absence include the type of program in which the student is enrolled and a standardized test in math.

We have attendance data on 314 high school juniors from two urban high schools in the file nb_data. The response variable of interest is days absent, daysabs. The variable math gives the standardized math score for each student. The variable prog is a three-level nominal variable indicating the type of instructional program in which the student is enrolled.

```{r}
ggplot(dat, aes(daysabs, fill = prog)) +
  geom_histogram(binwidth=1) +
  facet_grid(prog ~ ., margins=TRUE, scales="free")
```  
<!------------------------------------------------------------->

#### 6. Zero-Inflated Poisson Models

The state wildlife biologists want to model how many fish are being caught by fishermen at a state park. Visitors are asked how long they stayed, how many people were in the group, were there children in the group and how many fish were caught. Some visitors do not fish, but there is no data on whether a person fished or not. Some visitors who did fish did not catch any fish so there are excess zeros in the data because of the people that did not fish.

We have data on 250 groups that went to a park. Each group was questioned about how many fish they caught (count), how many children were in the group (child), how many people were in the group (persons), and whether or not they brought a camper to the park (camper).

In addition to predicting the number of fish caught, there is interest in predicting the existence of excess zeros, i.e., the probability that a group caught zero fish. We will use the variables child, persons, and camper in our model.

```{r}
## histogram with x axis in log10 scale
ggplot(zinb, aes(count)) + geom_histogram() + scale_x_log10()
```

```{r}
newdata1 <- expand.grid(0:3, factor(0:1), 1:4)
colnames(newdata1) <- c("child", "camper", "persons")
newdata1 <- subset(newdata1, subset=(child<=persons))
newdata1$phat <- predict(m1, newdata1)
```

```{r}
ggplot(newdata1, aes(x = child, y = phat, colour = factor(persons))) +
  geom_point() +
  geom_line() +
  facet_wrap(~camper) +
  labs(x = "Number of Children", y = "Predicted Fish Caught")
```
```{r}
zinb <- read.csv("http://www.ats.ucla.edu/stat/data/fish.csv")
zinb <- within(zinb, {
  nofish <- factor(nofish)
  livebait <- factor(livebait)
  camper <- factor(camper)
})
```
<pre><code>
summary(zinb)
##  nofish  livebait camper     persons         child             xb        
##  0:176   0: 34    0:103   Min.   :1.00   Min.   :0.000   Min.   :-3.275  
##  1: 74   1:216    1:147   1st Qu.:2.00   1st Qu.:0.000   1st Qu.: 0.008  
##                           Median :2.00   Median :0.000   Median : 0.955  
##                           Mean   :2.53   Mean   :0.684   Mean   : 0.974  
##                           3rd Qu.:4.00   3rd Qu.:1.000   3rd Qu.: 1.964  
##                           Max.   :4.00   Max.   :3.000   Max.   : 5.353  
##        zg             count      
##  Min.   :-5.626   Min.   :  0.0  
##  1st Qu.:-1.253   1st Qu.:  0.0  
##  Median : 0.605   Median :  0.0  
##  Mean   : 0.252   Mean   :  3.3  
##  3rd Qu.: 1.993   3rd Qu.:  2.0  
##  Max.   : 4.263   Max.   :149.0
## histogram with x axis in log10 scale
</code></pre>
```{r}
ggplot(zinb, aes(count, fill = camper)) +
  geom_histogram() +
  scale_x_log10() +
  facet_grid(camper ~ ., margins=TRUE, scales="free_y")
```
  
#### 7. Zero Truncated Negative Binomial Models

A study of length of hospital stay, in days, as a function of age, kind of health insurance and whether or not the patient died while in the hospital. Length of hospital stay is recorded as a minimum of at least one day. The study consists of 1,493 observations. 

The length of hospital stay variable is ***stay***. The variable ***age*** gives the age group from 1 to 9 which will be treated as interval in this example. The variables ***hmo*** and ***died*** are binary indicator variables for HMO insured patients and patients who died while in the hospital, respectively.

```{r}
ggplot(dat, aes(stay)) + geom_histogram() + scale_x_log10() + facet_grid(hmo ~ 
    died, margins = TRUE, scales = "free_y")
```

```{r}
ggplot(dat, aes(factor(age), stay)) +
  geom_violin() +
  geom_jitter(size=1.5) +
  scale_y_log10() +
  stat_smooth(aes(x = age, y = stay, group=1), method="loess")
```

```{r}
output <- data.frame(resid = resid(m1)[, 1], fitted = fitted(m1))
ggplot(output, aes(fitted, resid)) + geom_jitter(position = position_jitter(width = 0.25), 
    alpha = 0.5) + stat_smooth(method = "loess")
```

````{r}
ggplot(newdata, aes(x = age, y = yhat, colour = hmo))  +
  geom_point() +
  geom_line() +
  facet_wrap(~ died)
```
```{r}
## merge CIs with predicted values
newdata <- cbind(newdata, yhat)

## graph with CIs
ggplot(newdata, aes(x = age, y = yhat, colour = hmo, fill = hmo))  +
  geom_ribbon(aes(ymin = pLL, ymax = pUL), alpha = .25) +
  geom_point() +
  geom_line() +
  facet_wrap(~ died)
'''  

#### 8. Tobit Regression

```{r}
# function that gives the density of normal distribution
# for given mean and sd, scaled to be on a count metric
# for the histogram: count = density * sample size * bin width
f <- function(x, var, bw = 15) {
  dnorm(x, mean = mean(var), sd(var)) * length(var)  * bw
}

# setup base plot
p <- ggplot(dat, aes(x = apt, fill=prog))

# histogram, coloured by proportion in different programs
# with a normal distribution overlayed
p + stat_bin(binwidth=15) +
  stat_function(fun = f, size = 1,
    args = list(var = dat$apt))
    
p + stat_bin(binwidth = 1) + stat_function(fun = f, size = 1, args = list(var = dat$apt, 
    bw = 1))
# plot matrix
ggpairs(dat[, c("read", "math", "apt")])
```
#### 9. Truncated Regression

A study of students in a special GATE (gifted and talented education) program wishes to model achievement as a function of language skills and the type of program in which the student is currently enrolled. A major concern is that students are required to have a minimum achievement score of 40 to enter the special program. Thus, the sample is truncated at an achievement score of 40.


```{r}
dat <- read.dta("http://www.ats.ucla.edu/stat/data/truncreg.dta")

summary(dat)
##        id            achiv        langscore          prog    
##  Min.   :  3.0   Min.   :41.0   Min.   :31.0   general : 40  
##  1st Qu.: 55.2   1st Qu.:47.0   1st Qu.:47.5   academic:101  
##  Median :102.5   Median :52.0   Median :56.0   vocation: 37  
##  Mean   :103.6   Mean   :54.2   Mean   :54.0                 
##  3rd Qu.:151.8   3rd Qu.:63.0   3rd Qu.:61.8                 
##  Max.   :200.0   Max.   :76.0   Max.   :67.0
# histogram of achiv coloured by program type
ggplot(dat, aes(achiv, fill = prog)) +
  geom_histogram(binwidth=3)
```  

```{r}
# boxplot of achiv by program type
ggplot(dat, aes(prog, achiv)) +
  geom_boxplot() +
  geom_jitter()
```  


#### 10. Interval Regression

We wish to predict GPA from teacher ratings of effort, writing test scores and the type of program in which the student was enrolled (vocational, general or academic). The measure of GPA is a self-report response to the following item:

<pre><code>
Select the category that best represents your overall GPA.
  0.0 to 2.0
  2.0 to 2.5
  2.5 to 3.0
  3.0 to 3.4
  3.4 to 3.8
  3.8 to 4.0
  
</code></pre>  

```{r}
# bivariate plots
ggpairs(dat[, -1], lower = list(combo = "box"), upper = list(combo = "blank"))
```
