---
title: "``ggchisqtest``: Plot for Pearson's Chi-squared Test for Count Data"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(gginference)
```

#### Description
Visualise chi-squared contingency table tests and goodness-of-fit tests.

#### Usage

<pre><code>
ggchisqtest(t, colaccept="lightsteelblue1", colreject="gray84",
colstat="navyblue", alpha=0.05)
</code></pre>

#### Arguments
* ``t``: a list result of chisq.test of "htest" class
* ``colaccept``:  color the acceptance area of the test
* ``colreject``:  color for the rejection area of the test
* `` colstat``: color for the test statistic vline
* ``alpha``: default set to 0.05, choose confidence level for the plot as it is not stated in chisqtest

#### Examples
```{r}
## Chi-squared test for given probabilities
x <- c(A = 20, B = 15, C = 25)
chisq_test <- chisq.test(x)
chisq_test
ggchisqtest(chisq_test)
```
```{r}
x <- c(10, 86, 45, 38, 10)
p <- c(0.10, 0.40, 0.20, 0.20, 0.10)
chisq_test2 <- chisq.test(x, p = p)
chisq_test2
ggchisqtest(chisq_test2)
```
```{r}
## Pearson's Chi-squared test
library(MASS)
sex_smoke <- table(survey$Sex, survey$Smoke)
chisq_test3 <- chisq.test(sex_smoke)
chisq_test3
ggchisqtest(chisq_test3)
```

