
Autoplot survival::survfit

#### Description 
 
Autoplot survival::survfit

#### Usage 
 <pre><code>
## S3 method for class 'survfit'
autoplot(object, fun = NULL, surv.geom = "step",
surv.colour = NULL, surv.size = NULL, surv.linetype = NULL,
surv.alpha = NULL, surv.fill = NULL, surv.shape = NULL,
surv.connect = TRUE, conf.int = TRUE, conf.int.colour = "#0000FF",
conf.int.linetype = "none", conf.int.fill = "#000000",
conf.int.alpha = 0.3, censor = TRUE, censor.colour = NULL,
censor.size = 3, censor.alpha = NULL, censor.shape = "+",
facets = FALSE, nrow = NULL, ncol = 1, grid = FALSE,
strip_swap = FALSE, scales = "free_y", xlim = c(NA, NA), ylim = c(NA,
NA), log = "", main = NULL, xlab = NULL, ylab = NULL, asp = NULL,
...)

#### Arguments 
 
* object survival::survfit instance
* fun an arbitrary function defining a transformation of the survival curve
* surv.geom geometric string for survival curve. ’step’, ’line’ or ’point’
* surv.colour line colour for survival curve
* surv.size point size for survival curve
*``surv.linetype``: line type for survival curve
*``surv.alpha``: alpha for survival curve
*``surv.fill``: fill colour survival curve
*``surv.shape``: point shape survival curve
*``surv.connect``: logical frag indicates whether connects survival curve to the origin
*``conf.int``: Logical flag indicating whether to plot confidence intervals
*``conf.int.colour``: line colour for confidence intervals
*``conf.int.linetype``: line type for confidence intervals
*``conf.int.fill``: fill colour for confidence intervals
*``conf.int.alpha``: alpha for confidence intervals
* censor Logical flag indicating whether to plot censors
*``censor.colour``: colour for censors
*``censor.size``: size for censors
*``censor.alpha``: alpha for censors
* censor.shape shape for censors
* facets Logical value to specify use facets
* nrow Number of facet/subplot rows
* ncol Number of facet/subplot columns
* grid Logical flag indicating whether to draw grid
* strip_swap swap facet or grid strips
* scales Scale value passed to ggplot2
* xlim limits for x axis
* ylim limits for y axis
* log which variables to log transform ("x", "y", or "xy")
* ``main``:  character vector or expression for plot title
* ``xlab``:  character vector or expression for x axis label
* ``ylab``:  character vector or expression for y axis label
asp the y/x aspect ratio
* ``...``: other  arguments passed to methods

#### Examples 
```{r}
library(survival)
autoplot(survfit(Surv(time, status) ~ sex, data = lung))
autoplot(survfit(Surv(time, status) ~ sex, data = lung), facets = TRUE)
autoplot(survfit(Surv(time, status) ~ 1, data = lung))
```
```{r}
autoplot(survfit(Surv(time, status) ~ sex, data=lung), conf.int = FALSE, censor = FALSE)
autoplot(survfit(coxph(Surv(time, status) ~ sex, data = lung)))

```

#### Value
ggplot

