##``autoplot.forecast``
Autoplot forecast::forecast

#### Description 
 
Autoplot forecast::forecast

#### Usage 
 <pre><code>
## S3 method for class 'forecast'
autoplot(object, is.date = NULL, ts.connect = TRUE,
 predict.geom = "line", predict.colour = "#0000FF", predict.size = NULL,
 predict.linetype = NULL, predict.alpha = NULL, predict.fill = NULL,
 predict.shape = NULL, conf.int = TRUE, conf.int.colour = "#0000FF",
 conf.int.linetype = "none", conf.int.fill = "#000000",
 conf.int.alpha = 0.3, ...)
</code></pre>
#### Arguments 
 
* object forecast::forecast instance
* is.date Logical frag indicates whether the stats::ts is date or not. If not provided,
regard the input as date when the frequency is 4 or 12
* ts.connect Logical frag indicates whether connects original time-series and predicted values
* predict.geom geometric string for predicted time-series
* predict.colour line colour for predicted time-series
* predict.size point size for predicted time-series
* predict.linetype line type for predicted time-series14
* autoplot.ggmultiplot
* predict.alpha alpha for predicted time-series
* predict.fill fill colour for predicted time-series
* predict.shape point shape for predicted time-series
* conf.int Logical flag indicating whether to plot confidence intervals
* conf.int.colour line colour for confidence intervals
* conf.int.linetype line type for confidence intervals
* conf.int.fill fill colour for confidence intervals
* conf.int.alpha alpha for confidence intervals
...
other 
#### Arguments 
  passed to autoplot.ts
Value
ggplot

#### Examples 
```{r}
d.arima <- forecast::auto.arima(AirPassengers)
autoplot(forecast::forecast(d.arima, h = 10))
autoplot(forecast::forecast(d.arima, level = c(85), h = 10))
```
```{r}
autoplot(forecast::forecast(d.arima, h = 5), conf.int = FALSE, is.date = FALSE)
autoplot(forecast::forecast(stats::HoltWinters(UKgas), h = 10))
## Not run:
autoplot(forecast::forecast(forecast::ets(UKgas), h = 5))
## End(Not run)
```
