### Circles

Standard ggplot2 generally has you covered when it comes to drawing circles through the point geom, it does not make it possible to draw circles where the radius of the circles are related to the coordinate system. The geom_circle from ggforce are precisely for that. It generates a polygon resembling a circle based on a center point and a radius, making the radius directly readable from the axes. The geom are mainly intended to make it possible to draw circles with fine grained control, but will often not have any utility in itself. An exception would be in plotting trees as enclosure diagrams using circles. Here it will be necessary to have fine control over radius.

```{r}
# Here are some data describing some circles
circles <- data.frame(
    x0 = rep(1:3, 2),
    y0 =  rep(1:2, each=3),
    r = seq(0.1, 1, length.out = 6)
)
ggplot() + geom_circle(aes(x0=x0, y0=y0, r=r, fill=r), data=circles)
```

```{r}
# As it is related to the coordinate system, coord_fixed() is needed to ensure
# true circularity
ggplot() + geom_circle(aes(x0=x0, y0=y0, r=r, fill=r), data=circles) +
    coord_fixed()

```

```{r}

# Use n to set the smoothness of the circle
ggplot() + geom_circle(aes(x0=x0, y0=y0, r=r, fill=r), data=circles, n=10) +
    coord_fixed()

```
