
## Facets
Facets has been an integral part of the success of ggplot2. With v2.2 facets extensions finally became a possibility. While the idea of facets is to create small multiples of your plots based on a set of given variables in your data, extensions are not bound by this and they can be used for any type of layout work.
#### Pagination
When using facet_wrap() and facet_grid() with many-levelled variables you often end up with too small plots for any meaningful insight to be gained. ggforce provides a simple extension to both of the base facetting functions by allowing the plots to be split out into multiple pages. This is done by specifying the number of rows and columns on each page as well as which page to plot:
```{r}
# Standard facetting
ggplot(diamonds) +
  geom_point(aes(carat, price), alpha = 0.1) +
  facet_wrap(~cut:clarity, ncol = 3)
```

```{r}
# Pagination
ggplot(diamonds) +
  geom_point(aes(carat, price), alpha = 0.1) +
  facet_wrap_paginate(~cut:clarity, ncol = 3, nrow = 3, page = 1)
```

```{r}
# Works with grid as well
ggplot(diamonds) +
  geom_point(aes(carat, price), alpha = 0.1) +
  facet_grid_paginate(color~cut:clarity, ncol = 3, nrow = 3, page = 4)
```
A simple helper is provided to calculate the number of pages in a paginated plot
```{r}

p <- ggplot(diamonds) +
  geom_point(aes(carat, price), alpha = 0.1) +
  facet_wrap_paginate(~cut:clarity, ncol = 3, nrow = 3, page = 1)
n_pages(p)
## NULL
```
