---
title: "``ggRandomForest::calc_roc.rfsrc``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggRandomForests)
library(ggplot2)
```

calc_roc.rfsrc Reciever Operator Characteristic calculator

#### Description 

Reciever Operator Characteristic calculator

#### Usage 

<pre><code>

calc_roc.rfsrc(object, yvar, which.outcome = "all", oob = TRUE)

</code></pre>

#### Arguments

* ``object``: rfsrc or predict.rfsrc object containing predicted response
* ``yvar``: True response variable
* ``which.outcome``: If defined, only show ROC for this response.
* ``oob``: Use OOB estimates, the normal validation method (TRUE)

#### Examples 
```{r} 

## Taken from the gg_roc example
rfsrc_iris <- rfsrc(Species ~ ., data = iris)
#data(rfsrc_iris)
gg_dta <- calc_roc.rfsrc(rfsrc_iris, rfsrc_iris$yvar, which.outcome=1, oob=TRUE)
gg_dta <- calc_roc.rfsrc(rfsrc_iris, rfsrc_iris$yvar, which.outcome=1, oob=FALSE)

```

```{r}

ggplot(gg_dta,aes(x=(1-spec),y=sens)) + geom_line()
```

#### Details

For a randomForestSRC prediction and the actual response value, calculate the specificity (1-False
Positive Rate) and sensitivity (True Positive Rate) of a predictor.
This is a helper function for the ``gg_roc()`` functions, and not intended for use by the end user.

#### Value
A gg_roc object
See Also
calc_auc gg_roc plot.gg_roc
