
gg_error randomForestSRC error rate data object
#### Description 

Extract the cumulative (OOB) randomForestSRC error rate as a function of number of trees.
#### Usage 
<pre><code>

gg_error(object, ...)

</code></pre>
#### Arguments

object rfsrc object.
... optional arguments (not used).
Details
The gg_error function simply returns the rfsrc$err.rate object as a data.frame, and assigns the
class for connecting to the S3 plot.gg_error function.
Value
gg_error data.frame with one column indicating the tree number, and the remaining columns
from the rfsrc$err.rate return value.
gg_error 9


See Also
plot.gg_error rfsrc plot.rfsrc
#### Examples 
```{r} 

## #### Examples 
```{r} 
 from RFSRC package...
## ------------------------------------------------------------
## classification example
## ------------------------------------------------------------
## ------------- iris data
## You can build a randomForest
rfsrc_iris <- rfsrc(Species ~ ., data = iris)
# ... or load a cached randomForestSRC object
# data(rfsrc_iris, package="ggRandomForests")
# Get a data.frame containing error rates
gg_dta<- gg_error(rfsrc_iris)
# Plot the gg_error object
plot(gg_dta)
## ------------------------------------------------------------
## Regression example
## ------------------------------------------------------------
## Not run:
## ------------- airq data
rfsrc_airq <- rfsrc(Ozone ~ ., data = airquality, na.action = "na.impute")
# Get a data.frame containing error rates
gg_dta<- gg_error(rfsrc_airq)
# Plot the gg_error object
plot(gg_dta)
## End(Not run)
## Not run:
## ------------- Boston data
data(rfsrc_Boston, package="ggRandomForests")
# Get a data.frame containing error rates
gg_dta<- gg_error(rfsrc_Boston)
# Plot the gg_error object
plot(gg_dta)
## End(Not run)
## Not run:
## ------------- mtcars data
# Get a data.frame containing error rates
gg_dta<- gg_error(rfsrc_mtcars)
# Plot the gg_error object
plot(gg_dta)
## End(Not run)
## ------------------------------------------------------------
## Survival example
## ------------------------------------------------------------
## Not run:
## ------------- veteran data
## randomized trial of two treatment regimens for lung cancer
data(veteran, package = "randomForestSRC")
rfsrc_veteran <- rfsrc(Surv(time, status) ~ ., data = dta$veteran, ...)
gg_dta <- gg_error(rfsrc_veteran)
plot(gg_dta)
## End(Not run)
## Not run:
## ------------- pbc data
# Load a cached randomForestSRC object
data(rfsrc_pbc, package="ggRandomForests")
gg_dta <- gg_error(rfsrc_pbc)
plot(gg_dta)
## End(Not run)
