
gg_interaction Minimal Depth Variable Interaction data object
(find.interaction).
#### Description 

Converts the matrix returned from find.interaction to a data.frame and add attributes for S3
identification. If passed a rfsrc object, gg_interaction first runs the find.interaction function
with all optional 
</code></pre>
#### Arguments
.
#### Usage 
<pre><code>

gg_interaction(object, ...)
gg_interaction 11

</code></pre>
#### Arguments

object a rfsrc object or the output from the find.interaction function call.
... optional extra arguments
 passed to find.interaction.
Value
gg_interaction object

See Also
rfsrc find.interaction max.subtree var.select vimp plot.gg_interaction
#### Examples 
```{r} 

## #### Examples 
```{r} 
 from randomForestSRC package...
## ------------------------------------------------------------
## find interactions, classification setting
## ------------------------------------------------------------
## Not run:
## -------- iris data
## iris.obj <- rfsrc(Species ~., data = iris)
## TODO: VIMP interactions not handled yet....
## randomForestSRC::find.interaction(iris.obj, method = "vimp", nrep = 3)
## interaction_iris <- randomForestSRC::find.interaction(iris.obj)
data(interaction_iris, package="ggRandomForests")
gg_dta <- gg_interaction(interaction_iris)
plot(gg_dta, xvar="Petal.Width")
plot(gg_dta, panel=TRUE)
## End(Not run)
## ------------------------------------------------------------
## find interactions, regression setting
## ------------------------------------------------------------
## Not run:
## -------- air quality data
## airq.obj <- rfsrc(Ozone ~ ., data = airquality)
##
## TODO: VIMP interactions not handled yet....
## randomForestSRC::find.interaction(airq.obj, method = "vimp", nrep = 3)
## interaction_airq <- randomForestSRC::find.interaction(airq.obj)

data(interaction_airq, package="ggRandomForests")
gg_dta <- gg_interaction(interaction_airq)
plot(gg_dta, xvar="Temp")
plot(gg_dta, xvar="Solar.R")
plot(gg_dta, panel=TRUE)
## End(Not run)
## Not run:
## -------- Boston data
data(interaction_Boston, package="ggRandomForests")
gg_dta <- gg_interaction(interaction_Boston)
plot(gg_dta, panel=TRUE)
## End(Not run)
## Not run:
## -------- mtcars data
data(interaction_mtcars, package="ggRandomForests")
gg_dta <- gg_interaction(interaction_mtcars)
plot(gg_dta, panel=TRUE)
## End(Not run)
## ------------------------------------------------------------
## find interactions, survival setting
## ------------------------------------------------------------
## -------- pbc data
## data(pbc, package = "randomForestSRC")
## pbc.obj <- rfsrc(Surv(days,status) ~ ., pbc, nsplit = 10)
## interaction_pbc <- randomForestSRC::find.interaction(pbc.obj, nvar = 8)
## Not run:
data(interaction_pbc, package="ggRandomForests")
gg_dta <- gg_interaction(interaction_pbc)
plot(gg_dta, xvar="bili")
plot(gg_dta, panel=TRUE)
## End(Not run)
## Not run:
## -------- veteran data
data(interaction_veteran, package="ggRandomForests")
gg_dta <- gg_interaction(interaction_veteran)
plot(gg_dta, panel=TRUE)
## End(Not run)
