---
title: "``ggRandomForest::gg_minimal_vimp``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggRandomForests)
library(ggplot2)
```
 Minimal depth vs VIMP camparison by variable rankings.
#### Description 

Minimal depth vs VIMP camparison by variable rankings.
#### Usage 
<pre><code>

gg_minimal_vimp(object, ...)

</code></pre>
#### Arguments

object A rfsrc object, predict.rfsrc object or the list from the var.select.rfsrc
function.
... optional arguments
 passed to the var.select function if operating on an rfsrc
object.
@return gg_minimal_vimp comparison object.
@seealso plot.gg_minimal_vimp var.select
@aliases gg_minimal_vimp

#### Examples 

```{r} 

## Examples from RFSRC package...
## ------------------------------------------------------------
## classification example
## ------------------------------------------------------------
## Not run:
## -------- iris data
## You can build a randomForest
# rfsrc_iris <- rfsrc(Species ~ ., data = iris)
# varsel_iris <- randomForestSRC::var.select(rfsrc_iris)
# ... or load a cached randomForestSRC object
data(varsel_iris, package="ggRandomForests")
# Get a data.frame containing minimaldepth measures
gg_dta<- gg_minimal_vimp(varsel_iris)
# Plot the gg_minimal_depth object
plot(gg_dta)
```

```{r}
## ------------------------------------------------------------
## Regression example
## ------------------------------------------------------------
## Not run:
## -------- air quality data
# rfsrc_airq <- rfsrc(Ozone ~ ., data = airquality, na.action = "na.impute")
# varsel_airq <- randomForestSRC::var.select(rfsrc_airq)
# ... or load a cached randomForestSRC object
data(varsel_airq, package="ggRandomForests")
# Get a data.frame containing error rates
gg_dta<- gg_minimal_vimp(varsel_airq)
# Plot the gg_minimal_vimp object
plot(gg_dta)
## End(Not run)
## Not run:
## -------- Boston data
data(varsel_Boston, package="ggRandomForests")
# Get a data.frame containing error rates
gg_dta<- gg_minimal_vimp(varsel_Boston)
# Plot the gg_minimal_vimp object
plot(gg_dta)
## End(Not run)
```

```{r}
## -------- mtcars data
data(varsel_mtcars, package="ggRandomForests")
# Get a data.frame containing error rates
gg_dta<- gg_minimal_vimp(varsel_mtcars)
# Plot the gg_minimal_vimp object
plot(gg_dta)
## End(Not run)
## ------------------------------------------------------------
## Survival example
## ------------------------------------------------------------
```

```{r}
## -------- veteran data
## randomized trial of two treatment regimens for lung cancer
# data(veteran, package = "randomForestSRC")
# rfsrc_veteran <- rfsrc(Surv(time, status) ~ ., data = veteran, ntree = 100)
# varsel_veteran <- randomForestSRC::var.select(rfsrc_veteran)
# Load a cached randomForestSRC object
data(varsel_veteran, package="ggRandomForests")

gg_dta <- gg_minimal_vimp(varsel_veteran)
plot(gg_dta)
## End(Not run)
## Not run:
## -------- pbc data
data(varsel_pbc, package="ggRandomForests")
gg_dta <- gg_minimal_vimp(varsel_pbc)
plot(gg_dta)
## End(Not run)
```
