---
title: "gg_partial_coplot.rfsrc Data structures for stratified partial coplots"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggRandomForests)
library(randomForestSRC)
library(magrittr)
```


Description Data structures for stratified partial coplots

#### Usage
<pre><code>
## S3 method for class 'rfsrc' 
gg_partial_coplot(object, xvar, groups, 
  surv_type = c("mort", "rel.freq", "surv", "years.lost", "cif", "chf"),
  time, ...)
</code></pre>

#### Arguments 
* ``object``: rfsrc object
* ``xvar``: list of partial plot variables groups vector of strati???cation variable. 
* ``surv_type``: forsurvival random forests,``c("mort","rel.freq","surv","years.lost","cif","chf")`` 
* ``time``: vector of time points for survival random forests partial plots. 
* ``...``: extra arguments passed to plot.variable function

#### Value
gg_partial_coplot object. An subclass of a gg_partial_list object

#### Examples

```{r}
# Load the forest 
data(pbc, package = "randomForestSRC")
#rfsrc_pbc
```

```{r}
rfsrc_pbc <- rfsrc(Surv(days, status) ~ ., pbc, nsplit = 3)


# Create the variable plot. 
ggvar <- gg_variable(rfsrc_pbc, time = 45)
```
```{r}
ggvar %>% head()
```

```{r}
# Find intervals with similar number of observations. 
copper_cts <-quantile_pts(ggvar$copper, groups = 6, intervals = TRUE)
```
```{r}
# Create the conditional groups and add to the gg_variable object 
copper_grp <- cut(ggvar$copper, breaks = copper_cts)
```
```{r}
## We would run this, but it's expensive 
partial_coplot_pbc <- gg_partial_coplot(rfsrc_pbc, xvar = "bili", 
                                        groups = copper_grp, 
                                        surv_type = "surv", time = 50, show.plots = FALSE)
```
```{r}
## so load the cached set 
data(partial_coplot_pbc, package="ggRandomForests")
# Partial coplot 
```
```{r}
plot(partial_coplot_pbc) #, se = FALSE)
```