
``gg_roc.rfsrc`` ROC (Receiver operator curve) data from a classification random forest.

#### Description 

The sensitivity and specificity of a randomForests classification object.

#### Usage 
<pre><code>
## S3 method for class 'rfsrc'
gg_roc(object, which.outcome, oob = TRUE, ...)
</code></pre>

#### Arguments

* ``object``: an rfsrc classification object
* ``which.outcome``: select the classification outcome of interest.
* ``oob``: use oob estimates (default TRUE)
* ``...``: extra arguments (not used)

#### Examples 
```{r} 

## ------------------------------------------------------------
## classification example
## ------------------------------------------------------------
## -------- iris data
rfsrc_iris <- rfsrc(Species ~ ., data = iris)
#data(rfsrc_iris, package="ggRandomForests")
# ROC for setosa
gg_dta <- gg_roc(rfsrc_iris, which.outcome=1)
plot(gg_dta)
```

```{r}
# ROC for versicolor
gg_dta <- gg_roc(rfsrc_iris, which.outcome=2)
plot(gg_dta)
# ROC for virginica
gg_dta <- gg_roc(rfsrc_iris, which.outcome=3)
plot(gg_dta)
```


#### Value
gg_roc data.frame for plotting ROC curves.
See Also
plot.gg_roc rfsrc
