---
title: "gg_survival Nonparametric survival estimates."
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggRandomForests)
```


#### Description 

Nonparametric survival estimates.

#### Usage 

<pre><code>
gg_survival(interval = NULL, censor = NULL, by = NULL, data, type = c("kaplan", "nelson"), ...)
</code></pre>

#### Arguments 
* ``interval``: name of the interval variable in the training dataset. 
* ``censor``: name of the censoring variable in the training dataset. 
* ``by``: stratifying variable in the training dataset, defaults to  NULL 
* ``data``: name of the training data.frame type one of ("kaplan","nelson"), defaults to kaplan-meier 
* ``...``: extra arguments passed to kaplan or nelson functions.
* ``Details``: gg_survival is a wrapper function for generating nonparametric survival estimates using either nelson-aalen or kaplan-meier estimates.
* ``Value``: A gg_survival object created using the non-parametric kaplan-meier or nelson-aalon estimators.

#### Examples

```{r}
## Not run: ## -------- pbc data 
data(pbc, package="randomForestSRC") 
pbc$time <- pbc$days/364.25
```

```{r}
# This is the same as kaplan 
gg_dta <- gg_survival(interval="time", censor="status", data=pbc)
plot(gg_dta, error="none") 
```

```{r}
plot(gg_dta)
```

```{r}
# Stratified on treatment variable. 
gg_dta <- gg_survival(interval="time", censor="status", data=pbc, by="treatment")
plot(gg_dta, error="none") 
```

```{r}
plot(gg_dta)
```

```{r}
# ...with smaller confidence limits. 
gg_dta <- gg_survival(interval="time", censor="status", data=pbc, by="treatment", conf.int=.68)
plot(gg_dta, error="lines")
## End(Not run)
```
