
gg_variable Marginal variable depedance data object.
#### Description 

plot.variable generates a data.frame containing the marginal variable dependance or the partial variable dependence. The gg_variable function creates a data.frame of containing the full set of covariate data (predictor variables) and the predicted response for each observation. Marginal dependence figures are created using the plot.gg_variable function.

Optional  Arguments time point (or vector of points) of interest (for survival forests only) time.labels
If more than one time is specified, a vector of time labels for differentiating the time points (for survival
forests only) oob indicate if predicted results should include oob or full data set.
#### Usage 
<pre><code>

gg_variable(object, ...)

</code></pre>
#### Arguments

object a rfsrc object
... optional arguments

gg_variable 27
Details
The marginal variable dependence is determined by comparing relation between the predicted response
from the randomforest and a covariate of interest.
The gg_variable function operates on a rfsrc object, or the output from the plot.variable
function.

#### Value
gg_variable object
See Also
plot.gg_variable plot.variable
#### Examples 
```{r} 

## ------------------------------------------------------------
## classification
## ------------------------------------------------------------
## -------- iris data
## iris
rfsrc_iris <- rfsrc(Species ~., data = iris)
#data(rfsrc_iris, package="ggRandomForests")
gg_dta <- gg_variable(rfsrc_iris)
plot(gg_dta, xvar="Sepal.Width")
plot(gg_dta, xvar="Sepal.Length")
plot(gg_dta, xvar=rfsrc_iris$xvar.names,
panel=TRUE) # , se=FALSE)
## ------------------------------------------------------------
## regression
## ------------------------------------------------------------
## Not run:
## -------- air quality data
#rfsrc_airq <- rfsrc(Ozone ~ ., data = airquality)
data(rfsrc_airq, package="ggRandomForests")
gg_dta <- gg_variable(rfsrc_airq)
# an ordinal variable
gg_dta[,"Month"] <- factor(gg_dta[,"Month"])
plot(gg_dta, xvar="Wind")
plot(gg_dta, xvar="Temp")
plot(gg_dta, xvar="Solar.R")
plot(gg_dta, xvar=c("Solar.R", "Wind", "Temp", "Day"), panel=TRUE)
plot(gg_dta, xvar="Month", notch=TRUE)
28 gg_variable
## End(Not run)
## Not run:
## -------- motor trend cars data
#rfsrc_mtcars <- rfsrc(mpg ~ ., data = mtcars)
data(rfsrc_mtcars, package="ggRandomForests")
gg_dta <- gg_variable(rfsrc_mtcars)
# mtcars$cyl is an ordinal variable
gg_dta$cyl <- factor(gg_dta$cyl)
gg_dta$am <- factor(gg_dta$am)
gg_dta$vs <- factor(gg_dta$vs)
gg_dta$gear <- factor(gg_dta$gear)
gg_dta$carb <- factor(gg_dta$carb)
plot(gg_dta, xvar="cyl")
# Others are continuous
plot(gg_dta, xvar="disp")
plot(gg_dta, xvar="hp")
plot(gg_dta, xvar="wt")
# panels
plot(gg_dta,xvar=c("disp","hp", "drat", "wt", "qsec"), panel=TRUE)
plot(gg_dta, xvar=c("cyl", "vs", "am", "gear", "carb"), panel=TRUE, notch=TRUE)
## End(Not run)
```
## -------- Boston data
## ------------------------------------------------------------
## survival #### Examples 

```{r} 

## ------------------------------------------------------------
## Not run:
## -------- veteran data
## survival
# data(veteran, package = "randomForestSRC")
# rfsrc_veteran <- rfsrc(Surv(time,status)~., veteran, nsplit = 10, ntree = 100)
data(rfsrc_veteran, package="ggRandomForests")
# get the 1 year survival time.
gg_dta <- gg_variable(rfsrc_veteran, time=90)
# Generate variable dependance plots for age and diagtime
plot(gg_dta, xvar = "age")
plot(gg_dta, xvar = "diagtime", )
# Generate coplots
plot(gg_dta, xvar = c("age", "diagtime"), panel=TRUE, se=FALSE)
# If we want to compare survival at different time points, say 30, 90 day
# and 1 year
gg_dta <- gg_variable(rfsrc_veteran, time=c(30, 90, 365))
gg_vimp 29
# Generate variable dependance plots for age and diagtime
plot(gg_dta, xvar = "age")
## End(Not run)
## -------- pbc data
```
