---
title: "``ggRandomForest::gg_vimp``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggRandomForests)
library(ggplot2)
```
gg_vimp Variable Importance (VIMP) data object

#### Description 

gg_vimp Extracts the variable importance (VIMP) information from a a rfsrc object.
#### Usage 
<pre><code>

gg_vimp(object, nvar, ...)

</code></pre>
#### Arguments

object A rfsrc object or output from vimp
nvar argument to control the number of variables included in the output.
... arguments
 passed to the vimp.rfsrc function if the rfsrc object does not contain
importance information.

#### Value
gg_vimp object. A data.frame of VIMP measures, in rank order.

See Also
plot.gg_vimp rfsrc vimp
#### Examples 
```{r} 
## ------------------------------------------------------------
## classification example
## ------------------------------------------------------------
## -------- iris data
rfsrc_iris <- rfsrc(Species ~ ., data = iris)
#data(rfsrc_iris, package="ggRandomForests")
gg_dta <- gg_vimp(rfsrc_iris)
plot(gg_dta)
```


```{r}
## ------------------------------------------------------------
## regression example
## ------------------------------------------------------------

## -------- air quality data
# rfsrc_airq <- rfsrc(Ozone ~ ., airquality)
data(rfsrc_airq, package="ggRandomForests")
gg_dta <- gg_vimp(rfsrc_airq)
plot(gg_dta)
## End(Not run)
```


```{r}
## -------- Boston data
data(rfsrc_Boston, package="ggRandomForests")
gg_dta <- gg_vimp(rfsrc_Boston)
plot(gg_dta)
## End(Not run)
```


```{r}
## -------- mtcars data
data(rfsrc_mtcars, package="ggRandomForests")
gg_dta <- gg_vimp(rfsrc_mtcars)
plot(gg_dta)
```


```{r}
## ------------------------------------------------------------
## survival example
## ------------------------------------------------------------
## Not run:
## -------- veteran data
data(rfsrc_veteran, package="ggRandomForests")
gg_dta <- gg_vimp(rfsrc_veteran)
plot(gg_dta)
## End(Not run)
```


```{r}
## -------- pbc data
data(rfsrc_pbc, package="ggRandomForests")
gg_dta <- gg_vimp(rfsrc_pbc)
plot(gg_dta)
# Restrict to only the top 10.
gg_dta <- gg_vimp(rfsrc_pbc, nvar=10)
plot(gg_dta)
```
