---
title: "``ggRandomForest::kaplan``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggRandomForests)
library(ggplot2)
```
kaplan nonparametric kaplan-meier estimates


#### Description 

nonparametric kaplan-meier estimates
#### Usage 
<pre><code>

kaplan(interval, censor, data, by = NULL, ...)

</code></pre>
#### Arguments

interval name of the interval variable in the training dataset.
censor name of the censoring variable in the training dataset.
data name of the training set data.frame
by stratifying variable in the training dataset, defaults to NULL
... 
</code></pre>
#### Arguments
 passed to the survfit function
Value
gg_survival object
See Also
gg_survival nelson plot.gg_survival
#### Examples 
```{r} 
## Not run:
# These get run through the gg_survival #### Examples 

data(pbc, package="randomForestSRC")
pbc$time <- pbc$days/364.25
# This is the same as gg_survival
gg_dta <- kaplan(interval="time", censor="status",
data=pbc)
plot(gg_dta, error="none")
plot(gg_dta)
# Stratified on treatment variable.
gg_dta <- gg_survival(interval="time", censor="status",
data=pbc, by="treatment")
plot(gg_dta, error="none")
plot(gg_dta)
```
