---
title: "``ggRandomForest::nelson``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggRandomForests)
library(ggplot2)
```

nelson nonparametric Nelson-Aalen estimates
#### Description 

nonparametric Nelson-Aalen estimates
#### Usage 
<pre><code>

nelson(interval, censor, data, by = NULL, weight = NULL, ...)

</code></pre>
#### Arguments

* ``interval``: name of the interval variable in the training dataset.
* ``censor``: name of the censoring variable in the training dataset.
* ``data``: name of the survival training data.frame by stratifying variable in the training dataset, defaults to NULL
* ``weight``: for each observation (default=NULL)
* ``...``: arguments passed to the survfit function


#### Examples 
```{r} 

## Not run:
# These get run through the gg_survival  Examples 

data(pbc, package="randomForestSRC")
pbc$time <- pbc$days/364.25
# This is the same as gg_survival
gg_dta <- nelson(interval="time", censor="status",
data=pbc)
```
```{r}
plot(gg_dta, error="none")
plot(gg_dta)
```
```{r}
# Stratified on treatment variable.
gg_dta <- gg_survival(interval="time", censor="status",
data=pbc, by="treatment")
```
```{r}
plot(gg_dta, error="none")
plot(gg_dta, error="lines")
plot(gg_dta)
gg_dta <- gg_survival(interval="time", censor="status",
```
```{r}
data=pbc, by="treatment",
type="nelson")
plot(gg_dta, error="bars")
plot(gg_dta)
## End(Not run)
```
#### Value
gg_survival object
See Also
gg_survival nelson plot.gg_survival
partial.rfsr 33
