
plot.gg_variable Plot a gg_variable object,
#### Description 

Plot a gg_variable object,
#### Usage 
<pre><code>

## S3 method for class 'gg_variable'
plot(x, xvar, time, time_labels, panel = FALSE,
oob = TRUE, points = TRUE, smooth = TRUE, ...)

</code></pre>
#### Arguments

x gg_variable object created from a rfsrc object
xvar variable (or list of variables) of interest.
time For survival, one or more times of interest
time_labels string labels for times
panel Should plots be facetted along multiple xvar?
oob oob estimates (boolean)
points plot the raw data points (boolean)
smooth include a smooth curve (boolean)
... arguments
 passed to the ggplot2 functions.

#### Value
A single ggplot object, or list of ggplot objects


#### Examples 
```{r} 

## Not run:
## ------------------------------------------------------------
## classification
## ------------------------------------------------------------
## -------- iris data
## iris
#rfsrc_iris <- rfsrc(Species ~., data = iris)
data(rfsrc_iris, package="ggRandomForests")
gg_dta <- gg_variable(rfsrc_iris)
plot(gg_dta, xvar="Sepal.Width")
plot(gg_dta, xvar="Sepal.Length")
## !! TODO !! this needs to be corrected
plot(gg_dta, xvar=rfsrc_iris$xvar.names,
panel=TRUE, se=FALSE)
## ------------------------------------------------------------
## regression
## ------------------------------------------------------------
## -------- air quality data
#rfsrc_airq <- rfsrc(Ozone ~ ., data = airquality)
data(rfsrc_airq, package="ggRandomForests")
gg_dta <- gg_variable(rfsrc_airq)
# an ordinal variable
gg_dta[,"Month"] <- factor(gg_dta[,"Month"])
plot(gg_dta, xvar="Wind")
plot(gg_dta, xvar="Temp")
plot(gg_dta, xvar="Solar.R")
plot(gg_dta, xvar=c("Solar.R", "Wind", "Temp", "Day"), panel=TRUE)
plot(gg_dta, xvar="Month", notch=TRUE)
## -------- motor trend cars data
#rfsrc_mtcars <- rfsrc(mpg ~ ., data = mtcars)
data(rfsrc_mtcars, package="ggRandomForests")
gg_dta <- gg_variable(rfsrc_mtcars)
# mtcars$cyl is an ordinal variable
gg_dta$cyl <- factor(gg_dta$cyl)
gg_dta$am <- factor(gg_dta$am)
gg_dta$vs <- factor(gg_dta$vs)
gg_dta$gear <- factor(gg_dta$gear)
gg_dta$carb <- factor(gg_dta$carb)
plot(gg_dta, xvar="cyl")
# Others are continuous
plot.gg_vimp 57
plot(gg_dta, xvar="disp")
plot(gg_dta, xvar="hp")
plot(gg_dta, xvar="wt")
# panel
plot(gg_dta,xvar=c("disp","hp", "drat", "wt", "qsec"), panel=TRUE)
plot(gg_dta, xvar=c("cyl", "vs", "am", "gear", "carb") ,panel=TRUE)
## -------- Boston data
## ------------------------------------------------------------
## survival #### Examples 
```{r} 

## ------------------------------------------------------------
## -------- veteran data
## survival
data(veteran, package = "randomForestSRC")
rfsrc_veteran <- rfsrc(Surv(time,status)~., veteran, nsplit = 10, ntree = 100)
# get the 1 year survival time.
gg_dta <- gg_variable(rfsrc_veteran, time=90)
# Generate variable dependance plots for age and diagtime
plot(gg_dta, xvar = "age")
plot(gg_dta, xvar = "diagtime")
# Generate coplots
plot(gg_dta, xvar = c("age", "diagtime"), panel=TRUE)
# If we want to compare survival at different time points, say 30, 90 day
# and 1 year
gg_dta <- gg_variable(rfsrc_veteran, time=c(30, 90, 365))
# Generate variable dependance plots for age and diagtime
plot(gg_dta, xvar = "age")
plot(gg_dta, xvar = "diagtime")
# Generate coplots
plot(gg_dta, xvar = c("age", "diagtime"), panel=TRUE)
## -------- pbc data
## End(Not run)
