
plot.gg_partial_list Partial variable dependence plot, operates on a gg_partial_list object.
#### Description 

Generate a risk adjusted (partial) variable dependence plot. The function plots the rfsrc response
variable (y-axis) against the covariate of interest (specified when creating the gg_partial_list
object).
#### Usage 
<pre><code>

## S3 method for class 'gg_partial_list'
plot(x, points = TRUE, panel = FALSE, ...)

</code></pre>
#### Arguments

x gg_partial_list object created from a gg_partial forest object
points plot points (boolean) or a smooth line.
panel should the entire list be plotted together?
... extra 
</code></pre>
#### Arguments

Value
list of ggplot objects, or a single faceted ggplot object

See Also
plot.variable gg_partial plot.gg_partial gg_variable plot.gg_variable
#### Examples 
```{r} 

## Not run:
## ------------------------------------------------------------
## classification
## ------------------------------------------------------------
## -------- iris data
## iris "Petal.Width" partial dependence plot
##
plot.gg_partial_list 49
# rfsrc_iris <- rfsrc(Species ~., data = iris)
# partial_iris <- plot.variable(rfsrc_iris, xvar.names = "Petal.Width",
# partial=TRUE)
data(partial_iris, package="ggRandomForests")
gg_dta <- gg_partial(partial_iris)
plot(gg_dta)
## ------------------------------------------------------------
## regression
## ------------------------------------------------------------
## -------- air quality data
## airquality "Wind" partial dependence plot
##
# rfsrc_airq <- rfsrc(Ozone ~ ., data = airquality)
# partial_airq <- plot.variable(rfsrc_airq, xvar.names = "Wind",
# partial=TRUE, show.plot=FALSE)
data(partial_airq, package="ggRandomForests")
gg_dta <- gg_partial(partial_airq)
plot(gg_dta)
gg_dta.m <- gg_dta[["Month"]]
plot(gg_dta.m, notch=TRUE)
gg_dta[["Month"]] <- NULL
plot(gg_dta, panel=TRUE)
## -------- Boston data
data(partial_Boston, package="ggRandomForests")
gg_dta <- gg_partial(partial_Boston)
plot(gg_dta)
plot(gg_dta, panel=TRUE)
## -------- mtcars data
data(partial_mtcars, package="ggRandomForests")
gg_dta <- gg_partial(partial_mtcars)
plot(gg_dta)
gg_dta.cat <- gg_dta
gg_dta.cat[["disp"]] <- gg_dta.cat[["wt"]] <- gg_dta.cat[["hp"]] <- NULL
gg_dta.cat[["drat"]] <- gg_dta.cat[["carb"]] <- gg_dta.cat[["qsec"]] <- NULL
plot(gg_dta.cat, panel=TRUE)
gg_dta[["cyl"]] <- gg_dta[["vs"]] <- gg_dta[["am"]] <- NULL
gg_dta[["gear"]] <- NULL
plot(gg_dta, panel=TRUE)
## ------------------------------------------------------------
50 plot.gg_rfsrc
## survival #### Examples 
```{r} 

## ------------------------------------------------------------
## -------- veteran data
## survival "age" partial variable dependence plot
##
# data(veteran, package = "randomForestSRC")
# rfsrc_veteran <- rfsrc(Surv(time,status)~., veteran, nsplit = 10, ntree = 100)
#
## 30 day partial plot for age
# partial_veteran <- plot.variable(rfsrc_veteran, surv.type = "surv",
# partial = TRUE, time=30,
# xvar.names = "age",
# show.plots=FALSE)
data(partial_veteran, package="ggRandomForests")
gg_dta <- gg_partial(partial_veteran[[1]])
plot(gg_dta)
gg_dta.cat <- gg_dta
gg_dta[["celltype"]] <- gg_dta[["trt"]] <- gg_dta[["prior"]] <- NULL
plot(gg_dta, panel=TRUE)
gg_dta.cat[["karno"]] <- gg_dta.cat[["diagtime"]] <- gg_dta.cat[["age"]] <- NULL
plot(gg_dta.cat, panel=TRUE, notch=TRUE)
gg_dta <- lapply(partial_veteran, gg_partial)
length(gg_dta)
gg_dta <- combine.gg_partial(gg_dta[[1]], gg_dta[[2]] )
plot(gg_dta[["karno"]])
plot(gg_dta[["celltype"]])
gg_dta.cat <- gg_dta
gg_dta[["celltype"]] <- gg_dta[["trt"]] <- gg_dta[["prior"]] <- NULL
plot(gg_dta, panel=TRUE)
gg_dta.cat[["karno"]] <- gg_dta.cat[["diagtime"]] <- gg_dta.cat[["age"]] <- NULL
plot(gg_dta.cat, panel=TRUE, notch=TRUE)
## -------- pbc data
## End(Not run)
