
plot.gg_minimal_depth Plot a gg_minimal_depth object for random forest variable ranking.
plot.gg_minimal_depth 41
#### Description 

Plot a gg_minimal_depth object for random forest variable ranking.
#### Usage 
<pre><code>

## S3 method for class 'gg_minimal_depth'
plot(x, selection = FALSE, type = c("named",
"rank"), lbls, ...)

</code></pre>
#### Arguments

x gg_minimal_depth object created from a rfsrc object
selection should we restrict the plot to only include variables selected by the minimal
depth criteria (boolean).
type select type of y axis labels c("named","rank")
lbls a vector of alternative variable names.
... optional arguments
 passed to gg_minimal_depth
Value
ggplot object

See Also
var.select gg_minimal_depth
#### Examples 
```{r} 

## Not run:
## #### Examples 
```{r} 
 from RFSRC package...
## ------------------------------------------------------------
## classification example
## ------------------------------------------------------------
## -------- iris data
## You can build a randomForest
# rfsrc_iris <- rfsrc(Species ~ ., data = iris)
# varsel_iris <- var.select(rfsrc_iris)
# ... or load a cached randomForestSRC object
data(varsel_iris, package="ggRandomForests")
# Get a data.frame containing minimaldepth measures

gg_dta<- gg_minimal_depth(varsel_iris)
# Plot the gg_minimal_depth object
plot(gg_dta)
## ------------------------------------------------------------
## Regression example
## ------------------------------------------------------------
## -------- air quality data
# rfsrc_airq <- rfsrc(Ozone ~ ., data = airquality, na.action = "na.impute")
# varsel_airq <- var.select(rfsrc_airq)
# ... or load a cached randomForestSRC object
data(varsel_airq, package="ggRandomForests")
# Get a data.frame containing error rates
gg_dta<- gg_minimal_depth(varsel_airq)
# Plot the gg_minimal_depth object
plot(gg_dta)
## -------- Boston data
data(varsel_Boston, package="ggRandomForests")
# Get a data.frame containing error rates
plot(gg_minimal_depth(varsel_Boston))
## -------- mtcars data
data(varsel_mtcars, package="ggRandomForests")
# Get a data.frame containing error rates
plot.gg_minimal_depth(varsel_mtcars)
## ------------------------------------------------------------
## Survival example
## ------------------------------------------------------------
## -------- veteran data
## veteran data
## randomized trial of two treatment regimens for lung cancer
# data(veteran, package = "randomForestSRC")
# rfsrc_veteran <- rfsrc(Surv(time, status) ~ ., data = veteran, ntree = 100)
# varsel_veteran <- var.select(rfsrc_veteran)
# Load a cached randomForestSRC object
data(varsel_veteran, package="ggRandomForests")
gg_dta <- gg_minimal_depth(varsel_veteran)
plot(gg_dta)
## -------- pbc data
data(varsel_pbc, package="ggRandomForests")
gg_dta <- gg_minimal_depth(varsel_pbc)
plot(gg_dta)
plot.gg_minimal_vimp 43
## End(Not run)
