---
title: "``ggRandomForest::plot.gg_vimp``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggRandomForests)
library(ggplot2)
```

plot.gg_vimp Plot a gg_vimp object, extracted variable importance of a rfsrc object
#### Description 

Plot a gg_vimp object, extracted variable importance of a rfsrc object
#### Usage 
<pre><code>

## S3 method for class 'gg_vimp'
plot(x, relative, lbls, ...)

</code></pre>

#### Arguments
* x gg_vimp object created from a rfsrc object relative should we plot vimp or relative vimp. Defaults to vimp.
* lbls A vector of alternative variable labels. Item names should be the same as the variable names.
* ... optional arguments  passed to gg_vimp if necessary

#### Value
ggplot object

See Also
gg_vimp
#### Examples 
```{r} 

## Not run:
## ------------------------------------------------------------
## classification example
## ------------------------------------------------------------
## -------- iris data
# rfsrc_iris <- rfsrc(Species ~ ., data = iris)
data(rfsrc_iris, package="ggRandomForests")
gg_dta <- gg_vimp(rfsrc_iris)
plot(gg_dta)
## ------------------------------------------------------------
## regression example
## ------------------------------------------------------------
## -------- air quality data
# rfsrc_airq <- rfsrc(Ozone ~ ., airquality)
data(rfsrc_airq, package="ggRandomForests")
gg_dta <- gg_vimp(rfsrc_airq)
plot(gg_dta)
## -------- Boston data

data(rfsrc_Boston, package="ggRandomForests")
gg_dta <- gg_vimp(rfsrc_Boston)
plot(gg_dta)
## -------- mtcars data
data(rfsrc_mtcars, package="ggRandomForests")
gg_dta <- gg_vimp(rfsrc_mtcars)
plot(gg_dta)
## ------------------------------------------------------------
## survival example
## ------------------------------------------------------------
## -------- veteran data
data(rfsrc_veteran, package="ggRandomForests")
gg_dta <- gg_vimp(rfsrc_veteran)
plot(gg_dta)
## -------- pbc data
data(rfsrc_pbc, package="ggRandomForests")
gg_dta <- gg_vimp(rfsrc_pbc)
plot(gg_dta)
## End(Not run)
```
