---
title: "``ggRandomForest::gg_vimp``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggRandomForests)
library(ggplot2)
```
plot.gg_roc ROC plot generic function for a gg_roc object.
#### Description 

ROC plot generic function for a gg_roc object.
#### Usage 
<pre><code>

## S3 method for class 'gg_roc'
plot(x, which.outcome = NULL, ...)
plot.gg_roc 53

</code></pre>
#### Arguments

x gg_roc object created from a classification forest
which.outcome for multiclass problems, choose the class for plotting
... 
</code></pre>
#### Arguments
 passed to the gg_roc function
Value
ggplot object of the ROC curve

See Also
gg_roc rfsrc
#### Examples 
```{r} 
## Not run:
## ------------------------------------------------------------
## classification example
## ------------------------------------------------------------
## -------- iris data
#rfsrc_iris <- rfsrc(Species ~ ., data = iris)
data(rfsrc_iris, package="ggRandomForests")
# ROC for setosa
gg_dta <- gg_roc(rfsrc_iris, which.outcome=1)
plot.gg_roc(gg_dta)
# ROC for versicolor
gg_dta <- gg_roc(rfsrc_iris, which.outcome=2)
plot.gg_roc(gg_dta)
# ROC for virginica
gg_dta <- gg_roc(rfsrc_iris, which.outcome=3)
plot.gg_roc(gg_dta)
# Alternatively, you can plot all three outcomes in one go
# by calling the plot function on the forest object.
plot.gg_roc(rfsrc_iris)
## End(Not run)
```


```{r}
## ------------------------------------------------------------
## regression example
## ------------------------------------------------------------

## -------- air quality data
# rfsrc_airq <- rfsrc(Ozone ~ ., airquality)
data(rfsrc_airq, package="ggRandomForests")
gg_dta <- gg_vimp(rfsrc_airq)
plot(gg_dta)
## End(Not run)
```


```{r}
## -------- Boston data
data(rfsrc_Boston, package="ggRandomForests")
gg_dta <- gg_vimp(rfsrc_Boston)
plot(gg_dta)
## End(Not run)
```


```{r}
## -------- mtcars data
data(rfsrc_mtcars, package="ggRandomForests")
gg_dta <- gg_vimp(rfsrc_mtcars)
plot(gg_dta)
```


```{r}
## ------------------------------------------------------------
## survival example
## ------------------------------------------------------------
## Not run:
## -------- veteran data
data(rfsrc_veteran, package="ggRandomForests")
gg_dta <- gg_vimp(rfsrc_veteran)
plot(gg_dta)
## End(Not run)
```


```{r}
## -------- pbc data
data(rfsrc_pbc, package="ggRandomForests")
gg_dta <- gg_vimp(rfsrc_pbc)
plot(gg_dta)
# Restrict to only the top 10.
gg_dta <- gg_vimp(rfsrc_pbc, nvar=10)
plot(gg_dta)
```
