
plot.gg_rfsrc Predicted response plot from a gg_rfsrc object.
#### Description 

Plot the predicted response from a gg_rfsrc object, the rfsrc prediction, using the OOB prediction from the forest.
#### Usage 
<pre><code>

## S3 method for class 'gg_rfsrc'
plot(x, ...)

</code></pre>
#### Arguments
*  x gg_rfsrc object created from a rfsrc object
* ... arguments  passed to gg_rfsrc.

#### Value
ggplot object

See Also
gg_rfsrc rfsrc
#### Examples 
```{r} 

## Not run:
## ------------------------------------------------------------
## classification example
## ------------------------------------------------------------
## -------- iris data
# rfsrc_iris <- rfsrc(Species ~ ., data = iris)
data(rfsrc_iris, package="ggRandomForests")
gg_dta<- gg_rfsrc(rfsrc_iris)
plot(gg_dta)
```

```{r} 
## ------------------------------------------------------------
## Regression example
## ------------------------------------------------------------
## -------- air quality data
# rfsrc_airq <- rfsrc(Ozone ~ ., data = airquality, na.action = "na.impute")
data(rfsrc_airq, package="ggRandomForests")
gg_dta<- gg_rfsrc(rfsrc_airq)
plot(gg_dta)
## -------- Boston data
data(rfsrc_Boston, package="ggRandomForests")
plot(rfsrc_Boston)
```

```{r} 
## -------- mtcars data
data(rfsrc_mtcars, package="ggRandomForests")
gg_dta<- gg_rfsrc(rfsrc_mtcars)
plot(gg_dta)
## ------------------------------------------------------------
## Survival example
## ------------------------------------------------------------
## -------- veteran data
## randomized trial of two treatment regimens for lung cancer
# data(veteran, package = "randomForestSRC")
# rfsrc_veteran <- rfsrc(Surv(time, status) ~ ., data = veteran, ntree = 100)
data(rfsrc_veteran, package = "ggRandomForests")
gg_dta <- gg_rfsrc(rfsrc_veteran)
plot(gg_dta)
gg_dta <- gg_rfsrc(rfsrc_veteran, conf.int=.95)
plot(gg_dta)
gg_dta <- gg_rfsrc(rfsrc_veteran, by="trt")
plot(gg_dta)
```

```{r} 
## -------- pbc data
data(rfsrc_pbc, package = "ggRandomForests")
gg_dta <- gg_rfsrc(rfsrc_pbc)
plot(gg_dta)
gg_dta <- gg_rfsrc(rfsrc_pbc, conf.int=.95)
plot(gg_dta)
gg_dta <- gg_rfsrc(rfsrc_pbc, by="treatment")
plot(gg_dta)
## End(Not run)
```

