---
title: "ggRandomForest"
author: "Kevin O'Brien"
date: "14 October 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggRandomForests)
```

***Plot a gg_vimp object, extracted variable importance of a rfsrc object***

#### Description
Plot a gg_vimp object, extracted variable importance of a rfsrc object
plot.gg_vimp

#### Usage
<pre><code>
## S3 method for class 'gg_vimp'
plot(x, relative, lbls, ...)
</code></pre>

#### Arguments
* ``x`` ``gg_vimp`` object created from a rfsrc object
* ``relative`` should we plot vimp or relative vimp. 
 - Defaults to vimp.
* ``lbls`` A vector of alternative variable labels. 
 - Item names should be the same as the variable names.
* ``...`` optional arguments passed to ``gg_vimp`` if necessary

### Examples
```{r}

rfsrc_iris <- rfsrc(Species ~ ., data = iris)
data(rfsrc_iris, package="ggRandomForests")
gg_dta <- gg_vimp(rfsrc_iris)
plot(gg_dta)
```
```{r} 
# air quality data
rfsrc_airq <- rfsrc(Ozone ~ ., airquality)
data(rfsrc_airq, package="ggRandomForests")
gg_dta <- gg_vimp(rfsrc_airq)
plot(gg_dta)
```

### Boston Housing Example
<pre><code>
## -------- Boston dataprint.gg_minimal_depth
data(rfsrc_Boston, package="ggRandomForests")
gg_dta <- gg_vimp(rfsrc_Boston)
plot(gg_dta)
</code></pre>

```{r}
## -------- mtcars data
rfsrc_mtcars <- rfsrc(mpg ~ ., data = mtcars)
data(rfsrc_mtcars, package="ggRandomForests")
gg_dta <- gg_vimp(rfsrc_mtcars)
plot(gg_dta)
```

## survival example

<pre><code>
## -------- veteran data
data(rfsrc_veteran, package="ggRandomForests")
gg_dta <- gg_vimp(rfsrc_veteran)
plot(gg_dta)
</code></pre>
  
<pre><code>
## -------- pbc data
data(rfsrc_pbc, package="ggRandomForests")
gg_dta <- gg_vimp(rfsrc_pbc)
plot(gg_dta)
</code></pre>


#### References
* Breiman L. (2001). Random forests, Machine Learning, 45:5-32.
* Ishwaran H. and Kogalur U.B. (2007). Random survival forests for R, Rnews, 7(2):25-31.
* Ishwaran H. and Kogalur U.B. (2013). Random Forests for Survival, Regression and Classification (RF-SRC), R package version 1.4.
